---
title: "Cod diet: fine scale (rectangle) level diet index"
author: "Max Lindmark & Michele Casini"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Fit density (also referred to as CPUE) model with environmental predictors and use that to calculate weighted mean dissolved oxygen, temperature and depth of Baltic cod

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse); theme_set(theme_light(base_size = 12))
library(readxl)
library(tidylog)
library(RCurl)
library(viridis)
library(RColorBrewer)
library(patchwork)
library(janitor)
library(icesDatras)
library(mapdata)
library(patchwork)
library(rgdal)
library(raster)
library(sf)
library(rgeos)
library(chron)
library(lattice)
library(ncdf4)
library(marmap)
library(rnaturalearth)
library(rnaturalearthdata)
library(mapplots)
library(EnvStats)
library(qwraps2)
library(bayesplot)
library(tidybayes)
library(brms)
#remotes::install_github("pbs-assess/sdmTMB")
library(sdmTMB)

# To load entire cache in interactive r session, do: qwraps2::lazyload_cache_dir(path = "R/analysis/cod_flounder_diets_spatial_cache/html")
```

## For maps

```{r read coastline data, message=FALSE, warning=FALSE}
# Specify map ranges
ymin = 55; ymax = 58; xmin = 14; xmax = 20

map_data <- rnaturalearth::ne_countries(
  scale = "medium",
  returnclass = "sf", continent = "europe")

# Crop the polygon for plotting and efficiency:
# st_bbox(map_data) # find the rough coordinates
swe_coast <- suppressWarnings(suppressMessages(
  st_crop(map_data,
          c(xmin = xmin, ymin = ymin, xmax = xmax, ymax = ymax))))

# Transform our map into UTM 33 coordinates, which is the equal-area projection we fit in:
utm_zone33 <- 32633
swe_coast_proj <- sf::st_transform(swe_coast, crs = utm_zone33)

ggplot(swe_coast_proj) + geom_sf() 

# Define plotting theme for main plot
theme_plot <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
      axis.text.x = element_text(angle = 90),
      axis.text = element_text(size = 8),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 8),
      legend.position = "bottom",
      legend.key.height = unit(0.2, "cm"),
      legend.margin = margin(0, 0, 0, 0),
      legend.box.margin = margin(-5, -5, -5, -5),
      strip.text = element_text(size = 8, colour = 'black', margin = margin()),
      strip.background = element_rect(fill = "grey90")
      )
}

# Define plotting theme for facet_wrap map with years
theme_facet_map <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
        axis.text.x = element_text(angle = 90),
        axis.text = element_text(size = 6),
        strip.text = element_text(size = 8, colour = 'black', margin = margin()),
        strip.background = element_rect(fill = "grey90")
      )
}

# Make default base map plot
plot_map_raster <- 
ggplot(swe_coast_proj) + 
  geom_sf(size = 0.3) +
  labs(x = "Longitude", y = "Latitude") +
  theme_facet_map(base_size = 14)

# Function to convert from lat lon to UTM
LongLatToUTM <- function(x, y, zone){
  xy <- data.frame(ID = 1:length(x), X = x, Y = y)
  coordinates(xy) <- c("X", "Y")
  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
  return(as.data.frame(res))
}

theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA))
}
```

## Read and plot data

```{r read and plot data}
# These data are for total and prey specific stomach models
cod <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/cod_diet_analysis.csv") %>% dplyr::select(-X1)

cod <- cod %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(year > 2014) %>%
  filter(!quarter == 2) %>% 
  drop_na(predfle_density_sc, predcod_density_sc) %>% 
  droplevels()

fle <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/fle_diet_analysis.csv") %>% dplyr::select(-X1)

fle <- fle %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(!quarter == 2) %>% 
  drop_na(predfle_density_sc, predcod_density_sc) %>% 
  droplevels()

# These data are for the diet analysis (all prey groups)
cod_prey <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/cod_diet_full_analysis.csv") %>% dplyr::select(-X1) %>% mutate(species = "COD") %>% filter(year > 2014) %>% filter(!quarter == 2) %>% droplevels()

fle_prey <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/fle_diet_full_analysis.csv") %>% dplyr::select(-X1) %>% mutate(species = "FLE") %>% filter(!quarter == 2) %>% droplevels()

# Plot data in space
plot_map_raster +
  geom_point(data = fle_prey, aes(x = X * 1000, y = Y * 1000, color = "FLE"), alpha = 0.5) +
  geom_point(data = cod_prey, aes(x = X * 1000, y = Y * 1000, color = "COD"), alpha = 0.5) +
  theme_plot() +
  facet_wrap(~SD)

cod_prey <- cod_prey %>% filter(lat < 58)
fle_prey <- fle_prey %>% filter(lat < 58)
```

## Read the prediction grids

```{r read and process prediction grid, message=FALSE, warning=FALSE}
# And now read in pred_grid2 which has oxygen values at location and time and depth:
pred_grid2 <- readr::read_csv("https://raw.githubusercontent.com/maxlindmark/cod_interactions/main/data/pred_grid2.csv")

# Clean
pred_grid2 <- pred_grid2 %>%
  mutate(year = as.integer(year)) %>% 
  drop_na(depth)

# Add ices_rect
pred_grid2$ices_rect <- ices.rect2(pred_grid2$lon, pred_grid2$lat) 

# pred_grid2_q1 <- pred_grid2 %>% mutate(quarter = factor(1))
# pred_grid2_q4 <- pred_grid2 %>% mutate(quarter = factor(4))
```

## Calculate Schoener's and Levin's index for diet (by species, all sizes pooled)

```{r explore and calculate diet indicites}
# Reformat data to calculate Schoeners overlap index
# colnames(fle_prey)
fle_prey_long <- fle_prey %>%
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, ices_rect) %>%
  summarise(fle_stomach_content = sum(value)) %>% 
  arrange(name, year, ices_rect, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, ices_rect, sep = "_")) %>% 
  group_by(id) %>%
  mutate(fle_stomach_content_tot = sum(fle_stomach_content),
         fle_stomach_content_prop = fle_stomach_content / fle_stomach_content_tot) %>% 
  ungroup()

# This should amount to the number of unique prey
number_of_prey <- fle_prey_long %>% group_by(id) %>% mutate(n = n()) %>% ungroup() %>% distinct(n)
number_of_prey

test_id <- head(fle_prey_long$id, 1)
fle_prey_long %>% filter(id == test_id) %>% as.data.frame()

# Now cod
# colnames(cod_prey)
cod_prey_long <- cod_prey %>%
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, ices_rect) %>%
  summarise(cod_stomach_content = sum(value)) %>% 
  arrange(name, year, ices_rect, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, ices_rect, sep = "_")) %>% 
  group_by(id) %>%
  mutate(cod_stomach_content_tot = sum(cod_stomach_content),
         cod_stomach_content_prop = cod_stomach_content / cod_stomach_content_tot) %>% 
  ungroup()

unique(is.na(fle_prey_long))
unique(is.na(cod_prey_long))

fle_prey_long %>% mutate(fle_stomach_content_prop = replace_na(fle_stomach_content_prop, -9)) %>% filter(fle_stomach_content_prop == -9)
fle_prey_long <- fle_prey_long %>% mutate(fle_stomach_content_prop = replace_na(fle_stomach_content_prop, 0)) 

# Calculate Schoener index
schoener <- left_join(cod_prey_long, fle_prey_long) %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  drop_na(cod_stomach_content_prop) %>% 
  group_by(year, quarter, ices_rect) %>%
  summarise(schoener = 1 - 0.5*(sum(abs(fle_stomach_content_prop - cod_stomach_content_prop)))) %>% 
  ungroup()

# Calculate Levin niche index
levin <- left_join(cod_prey_long, fle_prey_long) %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  drop_na(cod_stomach_content_prop) %>% 
  group_by(year, quarter, ices_rect) %>% 
  summarise(levin_cod = (1/(number_of_prey$n-1)) * (((1/sum(cod_stomach_content_prop^2))) - 1),
            levin_fle = (1/(number_of_prey$n-1)) * (((1/sum(fle_stomach_content_prop^2))) - 1)) %>% 
  ungroup()

# Merge the indicies  
levin %>% arrange(desc(levin_fle))
levin <- levin %>% filter(levin_fle < 1)

ind <- left_join(levin, schoener)

# Summarise cod and flounder data by ices_rect then add to diet data
colnames(cod)
cod$year_rect_id <- paste(cod$year, cod$quarter, cod$ices_rect, sep = "_")

dens_sum <- cod %>% group_by(year_rect_id) %>%
  summarise(predfle_density_tot = sum(predfle_density),
            predcod_density_tot = sum(predcod_density)) %>% 
  ungroup() %>% 
  mutate(predfle_density_tot_sc = (predfle_density_tot - mean(predfle_density_tot)) / sd(predfle_density_tot),
         predcod_density_tot_sc = (predcod_density_tot - mean(predcod_density_tot)) / sd(predcod_density_tot))

ind$year_rect_id <- paste(ind$year, ind$quarter, ind$ices_rect, sep = "_")

ind <- left_join(ind, dens_sum)

# Summarise depth from the prediction grid then add to diet data
pred_grid2_sum <- pred_grid2 %>% 
  group_by(ices_rect) %>%
  summarise(mean_depth = mean(depth)) %>%
  mutate(depth_sc = (mean_depth - mean(mean_depth)) / sd(mean_depth)) %>% 
  ungroup()

ind <- left_join(ind, dplyr::select(pred_grid2_sum, ices_rect, depth_sc, mean_depth))

# Quickly check data to determine which distribution to use
ind %>% 
  ungroup() %>% 
  count(schoener == 0) %>% 
  mutate(prop = n / sum(n))

ind %>% 
  ungroup() %>% 
  count(levin_cod == 0) %>% 
  mutate(prop = n / sum(n))

ind %>% 
  ungroup() %>% 
  count(levin_fle == 0) %>% 
  mutate(prop = n / sum(n))

# Fit beta models, so few zeroes and no 1's
ind %>% arrange(desc(schoener)) %>% dplyr::select(schoener)
ind %>% arrange(desc(levin_cod)) %>% dplyr::select(levin_cod)
ind %>% arrange(desc(levin_fle)) %>% dplyr::select(levin_fle)

# Final polish of data before feeding into models (species, not size-based indicies)
ind <- ind %>% mutate(schoener2 = ifelse(schoener == 0, 0.0001, schoener),
                      levin_cod2 = ifelse(levin_cod == 0, 0.0001, levin_cod),
                      levin_fle2 = ifelse(levin_fle == 0, 0.0001, levin_fle),
                      year_f = as.factor(year),
                      quarter_f = as.factor(quarter),
                      ices_rect_f = as.factor(ices_rect))
```

### Calculate Schoener's overlap index for diet per size groups (cod 0-30, 30+ and all flounder sizes)

```{r Schoener per size group}
# colnames(cod_prey)
cod_prey_long2 <- cod_prey %>%
  mutate(size_group = ifelse(pred_cm > 30, "Large", "Small")) %>% 
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, ices_rect, size_group) %>%
  summarise(cod_stomach_content = sum(value)) %>% 
  arrange(name, year, ices_rect, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, ices_rect, sep = "_")) %>% 
  group_by(id, size_group) %>% # Add size-group here
  mutate(cod_stomach_content_tot = sum(cod_stomach_content),
         cod_stomach_content_prop = cod_stomach_content
         / cod_stomach_content_tot) %>% 
  ungroup()

# This should amount to the number of unique prey
cod_prey_long2 %>% group_by(id, size_group) %>% mutate(n = n()) %>% ungroup() %>% distinct(n)

# Split by size-group
cod_prey_long_small <- cod_prey_long2 %>% filter(size_group == "Small") %>%
  rename("cod_stomach_content_prop_small" = "cod_stomach_content_prop") %>%
  dplyr::select(name, id, cod_stomach_content_prop_small)

cod_prey_long_large <- cod_prey_long2 %>% filter(size_group == "Large") %>% 
  rename("cod_stomach_content_prop_large" = "cod_stomach_content_prop") %>%
  dplyr::select(name, id, cod_stomach_content_prop_large)

cod_prey_long_large %>% filter(cod_stomach_content_prop_large == "NaN")
cod_prey_long_small %>% filter(cod_stomach_content_prop_small == "NaN")
cod_prey_long_small <- cod_prey_long_small %>%
  mutate(cod_stomach_content_prop_small = ifelse(cod_stomach_content_prop_small == "NaN",
                                                 0,
                                                 cod_stomach_content_prop_small))

# Calculate Schoener index
schoener2 <- fle_prey_long %>%
  left_join(cod_prey_long_small) %>% 
  left_join(cod_prey_long_large) %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  drop_na(cod_stomach_content_prop_small) %>%
  drop_na(cod_stomach_content_prop_large) %>% 
  group_by(year, quarter, ices_rect) %>%
  summarise(schoener_f_sc = 1 - 0.5*(sum(abs(fle_stomach_content_prop - cod_stomach_content_prop_small))),
            schoener_f_lc = 1 - 0.5*(sum(abs(fle_stomach_content_prop - cod_stomach_content_prop_large))),
            schoener_sc_lc = 1 - 0.5*(sum(abs(cod_stomach_content_prop_small - cod_stomach_content_prop_large)))) %>% 
  ungroup()

schoener_long2 <- schoener2 %>% pivot_longer(4:6, names_to = "schoener_combination")

ggplot(schoener_long2, aes(schoener_combination, value, fill = factor(schoener_combination),
                           color = factor(schoener_combination))) +
  ggdist::stat_halfeye(adjust = 0.5, justification = -0.1, .width = 0, point_colour = NA, alpha = 0.8,
                       show.legend = FALSE) +
  geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5, show.legend = FALSE) +
  ggdist::stat_dots(side = "left", justification = 1.1, alpha = 0.8) + 
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2", name = "",
                    labels = c("Flounder-Cod (L)", "Flounder-Cod (S)", "Cod (S)-Cod (L)")) + 
  guides(color = FALSE, fill = guide_legend(override.aes = list(
    shape = 21, size = 2, fill = brewer.pal(n = 3, name = "Dark2"), color = brewer.pal(n = 3, name = "Dark2")))) +
  coord_flip() + 
  labs(y = "Value", x = "") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.y = element_blank()) +
  ggtitle("Schoeners's overlap index") + 
  NULL

ggsave("figures/schoener_size_groups_data.png", width = 6.5, height = 6.5, dpi = 600)

# Prepare for analysis
schoener_long2 <- schoener_long2 %>%
  mutate(value2 = ifelse(value == 0, 0.0001, value),
         value2 = ifelse(value == 1, 1-0.0001, value2),
         year_f = as.factor(year),
         quarter_f = as.factor(quarter),
         ices_rect_f = as.factor(ices_rect),
         schoener_combination_f = as.factor(schoener_combination))

# Add in average rectangle densities
dens_sum <- cod %>% group_by(year_rect_id) %>%
  summarise(predfle_density_tot = sum(predfle_density),
            predcod_density_tot = sum(predcod_density)) %>% 
  ungroup() %>% 
  mutate(predfle_density_tot_sc = (predfle_density_tot - mean(predfle_density_tot)) / sd(predfle_density_tot),
         predcod_density_tot_sc = (predcod_density_tot - mean(predcod_density_tot)) / sd(predcod_density_tot))

schoener_long2$year_rect_id <- paste(schoener_long2$year, schoener_long2$quarter, schoener_long2$ices_rect, sep = "_")

schoener_long2 <- left_join(schoener_long2, dens_sum)

# Summarize depth from the prediction grid then add to diet data
schoener_long2 <- left_join(schoener_long2, dplyr::select(pred_grid2_sum, ices_rect, depth_sc, mean_depth))
```

## Explore data (indicies)

```{r explore data}
# Plot sample size per id (rectangle, year, quarter)
fle_prey %>%
  filter(quarter == 1) %>% 
  group_by(year, quarter, ices_rect) %>%
  summarise(n = n()) %>% 
  ggplot(aes(year, n, fill = ices_rect)) +
  geom_bar(stat = "identity") + 
  facet_grid(~ ices_rect) + 
  coord_cartesian(expand = 0) + 
  guides(fill = FALSE) + 
  theme_plot()

fle_prey %>%
  filter(quarter == 4) %>% 
  group_by(year, quarter, ices_rect) %>%
  summarise(n = n()) %>% 
  ggplot(aes(year, n, fill = ices_rect)) +
  geom_bar(stat = "identity") + 
  facet_grid(~ ices_rect) + 
  coord_cartesian(expand = 0) + 
  guides(fill = FALSE) + 
  theme_plot()

cod_prey %>%
  filter(quarter == 1) %>% 
  group_by(year, quarter, ices_rect) %>%
  summarise(n = n()) %>% 
  ggplot(aes(year, n, fill = ices_rect)) +
  geom_bar(stat = "identity") + 
  facet_grid(~ ices_rect) + 
  coord_cartesian(expand = 0) + 
  guides(fill = FALSE) + 
  theme_plot()

cod_prey %>%
  filter(quarter == 4) %>% 
  group_by(year, quarter, ices_rect) %>%
  summarise(n = n()) %>% 
  ggplot(aes(year, n, fill = ices_rect)) +
  geom_bar(stat = "identity") + 
  facet_grid(~ ices_rect) + 
  coord_cartesian(expand = 0) + 
  guides(fill = FALSE) + 
  theme_plot()

# I'm running sensitivity analysis in the supp analysis where I aggregate data on sub-division level as well, to ensure larger samples sizes

# Plot the indicies
ggplot(ind) +
  geom_jitter(aes(factor(year), schoener),
              alpha = 0.8, width = 0.2, height = 0, size = 2)

ggplot(ind) +
  geom_jitter(aes(factor(year), levin_cod, color = "cod"),
              alpha = 0.8, width = 0.2, height = 0, size = 2) + 
  geom_jitter(aes(factor(year), levin_fle, color = "fle"),
              alpha = 0.8, width = 0.2, height = 0, size = 2) +
  scale_color_brewer(palette = "Dark2")

# Against response variables
# Schoener 
ggplot(ind, aes(x = predfle_density_tot + predcod_density_tot, y = schoener)) +
  geom_point() + stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter)
  
ggplot(ind, aes(x = predfle_density_tot, y = schoener)) + geom_point() + 
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter)

ggplot(ind, aes(x = predcod_density_tot, y = schoener)) + geom_point() +
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter)

# Now Levin
# Cod
ggplot(ind, aes(x = predfle_density_tot + predcod_density_tot, y = levin_cod)) +
  geom_point() + stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter) 
  
ggplot(ind, aes(x = predfle_density_tot, y = levin_cod)) + geom_point() +
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter) 
  
ggplot(ind, aes(x = predcod_density_tot, y = levin_cod)) + geom_point() + 
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter) 

# Flounder
ggplot(ind, aes(x = predfle_density_tot + predcod_density_tot, y = levin_fle)) +
  geom_point() + stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter) 
  
ggplot(ind, aes(x = predfle_density_tot, y = levin_fle)) + geom_point() +
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter) 
  
ggplot(ind, aes(x = predcod_density_tot, y = levin_fle)) + geom_point() + 
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3)) + facet_wrap(~quarter) 
```

# Fit `brms` models of diversity and overlap indices with densities as covariates to
## Beta model to schoener index

```{r fit beta models to schoener overlap with covariates, cache=TRUE}
# All covariates
m_schoen_beta_full <- brm(
  bf(schoener2 ~ 0 + year_f + depth_sc + predfle_density_tot_sc + predcod_density_tot_sc + quarter_f +
       (1|ices_rect_f),
     phi ~ 0 + quarter_f + depth_sc + predfle_density_tot_sc + predcod_density_tot_sc + year_f + 
       (1|ices_rect_f)),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

plot(m_schoen_beta_full)
conditional_effects(m_schoen_beta_full)
#loo_m_schoen_beta_full <- loo(m_schoen_beta_full, moment_match = TRUE)
#plot(loo_m_schoen_beta_full)

# Only density covariates
m_schoen_beta_dens <- brm(
  bf(schoener2 ~ 0 + year_f + predfle_density_tot_sc + predcod_density_tot_sc + quarter_f + (1|ices_rect_f),
     phi ~ 0 + year_f + predfle_density_tot_sc + predcod_density_tot_sc + quarter_f + (1|ices_rect_f)),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

plot(m_schoen_beta_dens)
conditional_effects(m_schoen_beta_dens)
#loo_m_schoen_beta_dens <- loo(m_schoen_beta_dens, moment_match = TRUE)
#plot(loo_m_schoen_beta_dens)

# Simplest model
m_schoen_beta <- brm(
  bf(schoener2 ~ 0 + year_f +  quarter_f + (1|ices_rect_f),
     phi ~ 0 + year_f + quarter_f + (1|ices_rect_f)),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

plot(m_schoen_beta)
conditional_effects(m_schoen_beta)
#loo_m_schoen_beta <- loo(m_schoen_beta, moment_match = TRUE)
#plot(loo_m_schoen_beta)

#loo_compare(loo_m_schoen_beta, loo_m_schoen_beta_dens, loo_m_schoen_beta_full)
```

### Plot

```{r plotting brms schoener models}
# Marginal effects are VERY tricky for logit beta models. I will therefore make my own prediction on a new data set using tidybayes and this blog: https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/#posterior-average-marginal-effects

# Evalute fit and convergence etc.
# PP check
pp_check(m_schoen_beta, ndraws = 50) +
  coord_cartesian(xlim = c(0, 0.15)) +
  scale_color_brewer(palette = "Dark2", name = "") +
  NULL

ggsave("figures/supp/schoener_pp_check.png", width = 6.5, height = 6.5, dpi = 600)

# Chain convergence
posterior <- as.array(m_schoen_beta)
dimnames(posterior)
pal_diag <- rev(brewer.pal(n = 4, name = "Dark2"))

mcmc_trace(posterior,
           pars = c("b_year_f2015", "b_year_f2016", "b_year_f2018", "b_year_f2019", "b_year_f2020",
                    "b_phi_year_f2015", "b_phi_year_f2016", "b_phi_year_f2017", "b_phi_year_f2018",
                    "b_phi_year_f2019", "b_phi_year_f2020"),
                 facet_args = list(ncol = 2, strip.position = "left")) +
  theme(text = element_text(size = 12), strip.text = element_text(size = 6),
        legend.position = "top") +
  scale_color_manual(values = alpha(pal_diag, alpha = 0.6))

ggsave("figures/supp/schoener_mcmc_trace.png", width = 6.5, height = 6.5, dpi = 600)

# Working with the posterior
posterior_beta <- m_schoen_beta_dens %>% 
  gather_draws(`b_.*`, regex = TRUE) %>% 
  mutate(component = ifelse(str_detect(.variable, "phi_"), "Precision", "Mean"),
         intercept = str_detect(.variable, "Intercept"))

ggplot(posterior_beta, aes(x = .value, y = fct_rev(.variable), fill = component)) +
  geom_vline(xintercept = 0, linetype = 2, alpha = 0.7) +
  stat_halfeye(aes(slab_alpha = intercept), alpha = 0.5,
               .width = c(0.8, 0.95), point_interval = "median_hdi") +
  scale_fill_brewer(palette = "Dark2") +
  scale_slab_alpha_discrete(range = c(1, 0.4)) +
  guides(fill = "none", slab_alpha = "none") +
  labs(x = "Coefficient", y = "Variable") +
  facet_wrap(vars(component), ncol = 1, scales = "free_y") +
  theme_plot() + 
  NULL

# Annual marginal effects (non dens model)
beta_schoen_pred_yr <- m_schoen_beta %>% 
  epred_draws(newdata = tibble(year_f = as.factor(c(2015:2020)),
                               quarter_f = factor(1)),
              re_formula = NA)

ggplot(beta_schoen_pred_yr, aes(x = .epred, y = year_f)) +
  stat_halfeye(.width = c(0.8, 0.95), alpha = 0.7, fill = "tomato2") +
  coord_cartesian(xlim = c(0, 0.4)) + 
  labs(x = "Predicted Schoener's overlap index", y = NULL
       , caption = "80% and 95% credible intervals shown in black"
       ) +
  NULL

ggsave("figures/schoener_annaul_epred.png", width = 6.5, height = 6.5, dpi = 600)

# Marginal effects of density (obviously with density model)
beta_schoen_pred_fle <- m_schoen_beta_dens %>% 
  epred_draws(newdata = tibble(predfle_density_tot_sc = 
                                 seq(min(ind$predfle_density_tot_sc),
                                     max(ind$predfle_density_tot_sc),
                                     length.out = 100),
                               year_f = factor(2015), 
                               quarter_f = factor(1), 
                               predcod_density_tot_sc = 0),
              re_formula = NA)

beta_schoen_pred_cod <- m_schoen_beta_dens %>% 
  epred_draws(newdata = tibble(predcod_density_tot_sc = 
                                 seq(min(ind$predcod_density_tot_sc),
                                     max(ind$predcod_density_tot_sc),
                                     length.out = 100),
                               year_f = factor(2015), 
                               quarter_f = factor(1), 
                               predfle_density_tot_sc = 0),
              re_formula = NA)

fle_marg <- ggplot(beta_schoen_pred_fle, aes(x = predfle_density_tot_sc, y = .epred)) +
  stat_lineribbon(aes(y = .epred), .width = c(0.5, 0.8)) +
  scale_fill_manual(values = c("grey85", "grey65")) +
  labs(y = "Predicted Schoener's overlap index", x = "Scaled flounder density"
       , caption = "80% and 95% credible intervals shown in black"
       ) +
  guides(fill = FALSE) + 
  NULL

cod_marg <- ggplot(beta_schoen_pred_cod, aes(x = predcod_density_tot_sc, y = .epred)) +
  stat_lineribbon(aes(y = .epred), .width = c(0.5, 0.8)) +
  scale_fill_manual(values = c("grey85", "grey65"), name = "Credible interval") +
  labs(y = "Predicted Schoener's overlap index", x = "Scaled cod density"
       , caption = "80% and 95% credible intervals shown in black"
       ) +
  theme(legend.position = "bottom",
        legend.direction = "horizontal") +
  NULL

fle_marg / cod_marg

ggsave("figures/schoener_cod_fle_marginal.png", width = 6.5, height = 6.5, dpi = 600)

# This is the brms way:
# conditional_effects(m_schoen_beta_dens, re_formula = NA, prob = 0.8, method = "posterior_epred",
#                     points = TRUE, rug = TRUE, effects = "predfle_density_tot_sc")
# 
# c_eff <- conditional_effects(m_schoen_beta_dens, re_formula = NA, prob = 0.8, method = "posterior_epred",
#                              effects = c("predfle_density_tot_sc", "predcod_density_tot_sc"))
# 
# ggplot(c_eff$predfle_density_tot_sc, aes(predfle_density_tot_sc, estimate__)) +
#   geom_ribbon(aes(ymin = lower__, ymax = upper__), fill = "gray80") +
#   geom_line() +
#   NULL
```

## Beta model to schoener index (by size)

```{r fit model of schoener by size, cache=TRUE}
# Simple model (no density)
m_schoen_size_beta <- brm(
  bf(value2 ~ 0 + schoener_combination_f + year_f + depth_sc + quarter_f + (1|ices_rect_f),
     phi ~ 0 + schoener_combination_f + year_f + depth_sc + quarter_f + (1|ices_rect_f)),
  data = schoener_long2, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.999))
```

### Plot

```{r plot schoener by size and species}
# Evaluate fit and convergence etc.
# PP check
pp_check(m_schoen_size_beta, ndraws = 50) +
  theme_light(base_size = 20) + 
  coord_cartesian(xlim = c(0, 0.15)) +
  scale_color_brewer(palette = "Dark2", name = "") +
  NULL

ggsave("figures/supp/schoener_size_pp_check.png", width = 6.5, height = 6.5, dpi = 600)

# Chain convergence
posterior <- as.array(m_schoen_size_beta)
dimnames(posterior)
pal_diag <- rev(brewer.pal(n = 4, name = "Dark2"))

mcmc_trace(posterior,
           pars = c("b_schoener_combination_fschoener_f_lc",
                    "b_schoener_combination_fschoener_f_sc",
                    "b_schoener_combination_fschoener_sc_lc",
                    "b_year_f2016", "b_year_f2017", "b_year_f2018",
                    "b_year_f2019", "b_year_f2020", "b_quarter_f4"),
                 facet_args = list(ncol = 2, strip.position = "left")) +
  theme(text = element_text(size = 12), strip.text = element_text(size = 4),
        legend.position = "top") +
  scale_color_manual(values = alpha(pal_diag, alpha = 0.6))

ggsave("figures/supp/schoener_size_mcmc_trace.png", width = 6.5, height = 6.5, dpi = 600)

# Working with the posterior
posterior_beta <- m_schoen_size_beta %>% 
  gather_draws(`b_.*`, regex = TRUE) %>% 
  mutate(component = ifelse(str_detect(.variable, "phi_"), "Precision", "Mean"),
         intercept = str_detect(.variable, "Intercept"))

ggplot(posterior_beta, aes(x = .value, y = fct_rev(.variable), fill = component)) +
  geom_vline(xintercept = 0, linetype = 2, alpha = 0.7) +
  stat_halfeye(aes(slab_alpha = intercept), alpha = 0.5,
               .width = c(0.8, 0.95), point_interval = "median_hdi") +
  scale_fill_brewer(palette = "Dark2") +
  scale_slab_alpha_discrete(range = c(1, 0.4)) +
  guides(fill = "none", slab_alpha = "none") +
  labs(x = "Coefficient", y = "Variable") +
  facet_wrap(vars(component), ncol = 1, scales = "free_y") +
  theme_plot() + 
  NULL

# Marginal effects of Schoener combination variable
beta_schoen_pred_size <- m_schoen_size_beta %>% 
  epred_draws(newdata = tibble(schoener_combination_f = c("schoener_f_sc", "schoener_f_lc", "schoener_sc_lc"),
                               depth_sc = 0, 
                               year_f = factor(2015),
                               quarter_f = factor(1)),
              re_formula = NA) %>% 
  mutate(schoener_combination_f = ifelse(schoener_combination_f == "schoener_f_sc", 
                                         "Flounder-Cod (S)", schoener_combination_f),
         schoener_combination_f = ifelse(schoener_combination_f == "schoener_f_lc", 
                                         "Flounder-Cod (L)", schoener_combination_f),
         schoener_combination_f = ifelse(schoener_combination_f == "schoener_sc_lc", 
                                         "Cod (S)-Cod (L)", schoener_combination_f))

ggplot(beta_schoen_pred_size, aes(x = .epred, fill = schoener_combination_f)) +
  stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi", alpha = 0.5,
               adjust = 2, position = position_dodge(width = 0.0075)) +
  coord_cartesian(ylim = c(0, 0.3)) +
  scale_fill_brewer(palette = "Dark2", name = "Species-size combination") +
  theme_light(base_size = 16) +
  theme(legend.position = "top") +
  geom_vline(xintercept = 0.6, linetype = 2, color = "gray20") +
  guides(fill = guide_legend(title.position = "top", title.hjust = 0.5)) +
  labs(x = "Predicted Schoener's overlap index", y = NULL
       , caption = "80% and 95% credible intervals shown in black"
       ) +
  NULL

ggsave("figures/schoener_size_marginal.png", width = 6.5, height = 6.5, dpi = 600)
```

## Beta model to levin index

```{r fit beta models to levin diversity index with covariates, cache=TRUE}
# Cod Levin index: all covariates
m_levin_beta_full_cod <- brm(
  bf(levin_cod2 ~ 0 + year_f + quarter_f + depth_sc + predfle_density_tot_sc + predcod_density_tot_sc + (1|ices_rect_f),
     phi ~ 0 + year_f + quarter_f + depth_sc + predfle_density_tot_sc + predcod_density_tot_sc),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

# No density covars
m_levin_beta_cod <- brm(
  bf(levin_cod2 ~ 0 + year_f + quarter_f + depth_sc + (1|ices_rect_f),
     phi ~ 0 + year_f + quarter_f + depth_sc),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

# no good convergence in this model!

# Compare models with or without density covariates
loo_compare(loo(m_levin_beta_full_cod, moment_match = TRUE),
            loo(m_levin_beta_cod, moment_match = TRUE))

# Fle Levin index: all covariates
m_levin_beta_full_fle <- brm(
  bf(levin_fle2 ~ 0 + year_f + quarter_f + depth_sc + predfle_density_tot_sc + predcod_density_tot_sc + (1|ices_rect_f),
     phi ~ 0 + year_f),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

# No density covars
m_levin_beta_fle <- brm(
  bf(levin_fle2 ~ 0 + year_f + quarter_f + depth_sc + (1|ices_rect_f),
     phi ~ 0 + year_f),
  data = ind, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

# Compare models with or without density covariates
loo_compare(loo(m_levin_beta_full_fle),
            loo(m_levin_beta_fle))
```

```{r test pooling levin and add species as covariate}
# All Levin's as response, species as covariate? No density covariates!
hist(ind$levin_fle)
hist(ind$levin_cod)
colnames(ind)
ind2 <- ind %>% pivot_longer(4:5, names_to = "species", values_to = "levins")
colnames(ind2)

m_levin_beta <- brm(
  bf(levin_fle2 ~ 0 + species + year_f + quarter_f + depth_sc + (1|ices_rect_f),
     phi ~ 0 + year_f),
  data = ind2, family = brms::Beta(link = "logit", link_phi = "log"), save_pars = save_pars(all = TRUE),
  chains = 4, iter = 4000, warmup = 1000, cores = 4, control = list(adapt_delta = 0.99))

summary(m_levin_beta)
plot(m_levin_beta)

# Marginal effect of species
beta_levin_pred_species <- m_levin_beta %>% 
  epred_draws(newdata = tibble(species = c("levin_cod", "levin_fle"),
                               year_f = factor(2015),
                               depth_sc = 0,
                               quarter_f = factor(1)),
              re_formula = NA) %>% 
  mutate(species = ifelse(species == "levin_cod", "Cod", "Flounder"))

ggplot(beta_levin_pred_species, aes(x = .epred, fill = species)) +
  stat_halfeye(.width = c(0.8, 0.95), point_interval = "median_hdi", alpha = 0.5, 
               adjust = 2, position = position_dodge(width = 0.0075)) + 
  coord_cartesian(ylim = c(0, 0.5)) +
  scale_fill_brewer(palette = "Dark2", name = "Species") +
  theme_light(base_size = 16) +
  theme(legend.position = "top") +
  guides(fill = guide_legend(title.position = "top", title.hjust = 0.5)) +
  labs(x = "Predicted Levins's diversity index", y = NULL
       , caption = "80% and 95% credible intervals shown in black"
       ) +
  NULL
```

```{r}
knitr::knit_exit()
```
