---
title: "Cod diet: spatial analysis of cod and flounder diets in relation to density"
author: "Max Lindmark & Michele Casini"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Fit density (also referred to as CPUE) model with environmental predictors and use that to calculate weighted mean dissolved oxygen, temperature and depth of Baltic cod

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse); theme_set(theme_light(base_size = 12))
library(readxl)
library(tidylog)
library(RCurl)
library(viridis)
library(RColorBrewer)
library(patchwork)
library(janitor)
library(icesDatras)
library(mapdata)
library(patchwork)
library(rgdal)
library(raster)
library(sf)
library(rgeos)
library(chron)
library(lattice)
library(ncdf4)
library(marmap)
library(rnaturalearth)
library(rnaturalearthdata)
library(mapplots)
library(EnvStats)
library(qwraps2)
library(bayesplot)
library(tidybayes)
library(brms)
#remotes::install_github("pbs-assess/sdmTMB")
library(sdmTMB)

# To load entire cache in interactive r session, do: qwraps2::lazyload_cache_dir(path = "R/analysis/cod_flounder_diets_spatial_cache/html")
```

## For maps

```{r read coastline data, message=FALSE, warning=FALSE}
# Specify map ranges
ymin = 55; ymax = 58; xmin = 14; xmax = 20

map_data <- rnaturalearth::ne_countries(
  scale = "medium",
  returnclass = "sf", continent = "europe")

# Crop the polygon for plotting and efficiency:
# st_bbox(map_data) # find the rough coordinates
swe_coast <- suppressWarnings(suppressMessages(
  st_crop(map_data,
          c(xmin = xmin, ymin = ymin, xmax = xmax, ymax = ymax))))

# Transform our map into UTM 33 coordinates, which is the equal-area projection we fit in:
utm_zone33 <- 32633
swe_coast_proj <- sf::st_transform(swe_coast, crs = utm_zone33)

ggplot(swe_coast_proj) + geom_sf() 

# Define plotting theme for main plot
theme_plot <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
      axis.text.x = element_text(angle = 90),
      axis.text = element_text(size = 8),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 8),
      legend.position = "bottom",
      legend.key.height = unit(0.2, "cm"),
      legend.margin = margin(0, 0, 0, 0),
      legend.box.margin = margin(-5, -5, -5, -5),
      strip.text = element_text(size = 8, colour = 'black', margin = margin()),
      strip.background = element_rect(fill = "grey90")
      )
}

# Define plotting theme for facet_wrap map with years
theme_facet_map <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
        axis.text.x = element_text(angle = 90),
        axis.text = element_text(size = 6),
        strip.text = element_text(size = 8, colour = 'black', margin = margin()),
        strip.background = element_rect(fill = "grey90")
      )
}

# Make default base map plot
plot_map_raster <- 
ggplot(swe_coast_proj) + 
  geom_sf(size = 0.3) +
  labs(x = "Longitude", y = "Latitude") +
  theme_facet_map(base_size = 14)

# Function to convert from lat lon to UTM
LongLatToUTM <- function(x, y, zone){
  xy <- data.frame(ID = 1:length(x), X = x, Y = y)
  coordinates(xy) <- c("X", "Y")
  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
  return(as.data.frame(res))
}

theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA))
}
```

## Read and plot data

```{r read and plot data}
# These data are for total and prey specific stomach models
cod <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/cod_diet_analysis.csv") %>% dplyr::select(-X1)

cod <- cod %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(year > 2014) %>%
  filter(!quarter == 2) %>% 
  drop_na(predfle_density_sc, predcod_density_sc) %>% 
  droplevels()

fle <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/fle_diet_analysis.csv") %>% dplyr::select(-X1)

fle <- fle %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(!quarter == 2) %>% 
  drop_na(predfle_density_sc, predcod_density_sc) %>% 
  droplevels()

# These data are for the diet index analysis (all prey groups)
cod_prey <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/cod_diet_full_analysis.csv") %>% dplyr::select(-X1) %>% mutate(species = "COD") %>% filter(year > 2014) %>% filter(!quarter == 2) %>% droplevels()

fle_prey <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/fle_diet_full_analysis.csv") %>% dplyr::select(-X1) %>% mutate(species = "FLE") %>% filter(!quarter == 2) %>% droplevels()

# Plot data in space
plot_map_raster +
  geom_point(data = fle_prey, aes(x = X * 1000, y = Y * 1000, color = "FLE"), alpha = 0.5) +
  geom_point(data = cod_prey, aes(x = X * 1000, y = Y * 1000, color = "COD"), alpha = 0.5) +
  theme_plot() +
  facet_wrap(~sub_div)

cod_prey <- cod_prey %>% filter(lat < 58)
fle_prey <- fle_prey %>% filter(lat < 58)

# I will also make a new area category, pooling 24 and 25, and 27-8, making it a southwest (coastal), north (coastal) and offshore (26). Note this is only for the cod_prey and fle_prey data, which we use for indicies. The other stomach analysis is spatial, but here we need enough samples to calculate indicies properly
cod_prey <- cod_prey %>% mutate(area = ifelse(sub_div %in% c(24, 25), "24-25", NA),
                                area = ifelse(sub_div %in% c(27, 28), "27, 28", area),
                                area = ifelse(sub_div == 26, "26", area))

fle_prey <- fle_prey %>% mutate(area = ifelse(sub_div %in% c(24, 25), "24-25", NA),
                                area = ifelse(sub_div %in% c(27, 28), "27, 28", area),
                                area = ifelse(sub_div == 26, "26", area))
```

## Read the prediction grids

```{r read and process prediction grid, message=FALSE, warning=FALSE}
# And now read in pred_grid2 which has oxygen values at location and time and depth:
pred_grid2 <- readr::read_csv("https://raw.githubusercontent.com/maxlindmark/cod_interactions/main/data/pred_grid2.csv")

# Clean
pred_grid2 <- pred_grid2 %>%
  mutate(year = as.integer(year)) %>% 
  drop_na(depth)

# Add ices_rect
pred_grid2$ices_rect <- ices.rect2(pred_grid2$lon, pred_grid2$lat) 

# pred_grid2_q1 <- pred_grid2 %>% mutate(quarter = factor(1))
# pred_grid2_q4 <- pred_grid2 %>% mutate(quarter = factor(4))
```

## Calculate Schoener's and Levin's index for diet (by species, all sizes pooled)

```{r explore and calculate diet indicites}
# Reformat data to calculate Schoeners overlap index
# colnames(fle_prey)
fle_prey_long <- fle_prey %>%
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, area) %>%
  summarise(fle_stomach_content = sum(value)) %>% 
  arrange(name, year, area, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, area, sep = "_")) %>% 
  group_by(id) %>%
  mutate(fle_stomach_content_tot = sum(fle_stomach_content),
         fle_stomach_content_prop = fle_stomach_content / fle_stomach_content_tot) %>% 
  ungroup()

# This should amount to the number of unique prey
number_of_prey <- fle_prey_long %>% group_by(id) %>% mutate(n = n()) %>% ungroup() %>% distinct(n)
number_of_prey

test_id <- head(fle_prey_long$id, 1)
fle_prey_long %>% filter(id == test_id) %>% as.data.frame()

# Now cod
# colnames(cod_prey)
cod_prey_long <- cod_prey %>%
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, area) %>%
  summarise(cod_stomach_content = sum(value)) %>% 
  arrange(name, year, area, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, area, sep = "_")) %>% 
  group_by(id) %>%
  mutate(cod_stomach_content_tot = sum(cod_stomach_content),
         cod_stomach_content_prop = cod_stomach_content / cod_stomach_content_tot) %>% 
  ungroup()

unique(is.na(fle_prey_long))
unique(is.na(cod_prey_long))

fle_prey_long %>% mutate(fle_stomach_content_prop = replace_na(fle_stomach_content_prop, -9)) %>% filter(fle_stomach_content_prop == -9)
fle_prey_long <- fle_prey_long %>% mutate(fle_stomach_content_prop = replace_na(fle_stomach_content_prop, 0)) 

# Calculate Schoener index
schoener <- left_join(cod_prey_long, fle_prey_long) %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  drop_na(cod_stomach_content_prop) %>% 
  group_by(year, quarter, area) %>%
  summarise(schoener = 1 - 0.5*(sum(abs(fle_stomach_content_prop - cod_stomach_content_prop)))) %>% 
  ungroup()

# Calculate Levin niche index
levin <- left_join(cod_prey_long, fle_prey_long) %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  drop_na(cod_stomach_content_prop) %>% 
  group_by(year, quarter, area) %>% 
  summarise(levin_cod = (1/(number_of_prey$n-1)) * (((1/sum(cod_stomach_content_prop^2))) - 1),
            levin_fle = (1/(number_of_prey$n-1)) * (((1/sum(fle_stomach_content_prop^2))) - 1)) %>% 
  ungroup()

# Merge the indicies  
levin %>% arrange(desc(levin_fle))
levin <- levin %>% filter(levin_fle < 1)

ind <- left_join(levin, schoener)

# Summarise cod and flounder data by area then add to diet data
# colnames(cod)
# cod$year_area_id <- paste(cod$year, cod$quarter, cod$area, sep = "_")
# 
# dens_sum <- cod %>% group_by(year_area_id) %>%
#   summarise(predfle_density_tot = sum(predfle_density),
#             predcod_density_tot = sum(predcod_density)) %>% 
#   ungroup() %>% 
#   mutate(predfle_density_tot_sc = (predfle_density_tot - mean(predfle_density_tot)) / sd(predfle_density_tot),
#          predcod_density_tot_sc = (predcod_density_tot - mean(predcod_density_tot)) / sd(predcod_density_tot))
# 
# ind$year_area_id <- paste(ind$year, ind$quarter, ind$area, sep = "_")
# 
# ind <- left_join(ind, dens_sum)

# Quickly check data to determine which distribution to use
ind %>% 
  ungroup() %>% 
  count(schoener == 0) %>% 
  mutate(prop = n / sum(n))

ind %>% 
  ungroup() %>% 
  count(levin_cod == 0) %>% 
  mutate(prop = n / sum(n))

ind %>% 
  ungroup() %>% 
  count(levin_fle == 0) %>% 
  mutate(prop = n / sum(n))

# Fit beta models, so few zeroes and no 1's
ind %>% arrange(desc(schoener)) %>% dplyr::select(schoener)
ind %>% arrange(desc(levin_cod)) %>% dplyr::select(levin_cod)
ind %>% arrange(desc(levin_fle)) %>% dplyr::select(levin_fle)

# Final polish of data before feeding into models (species, not size-based indicies)
ind <- ind %>% mutate(schoener2 = ifelse(schoener == 0, 0.0001, schoener),
                      levin_cod2 = ifelse(levin_cod == 0, 0.0001, levin_cod),
                      levin_fle2 = ifelse(levin_fle == 0, 0.0001, levin_fle),
                      year_f = as.factor(year),
                      quarter_f = as.factor(quarter),
                      area_f = as.factor(area))
```

### Calculate Schoener's overlap index for diet per size groups (cod 0-30, 30+ and all flounder sizes)

```{r Schoener per size group}
# colnames(cod_prey)
cod_prey_long2 <- cod_prey %>%
  mutate(size_group = ifelse(pred_cm > 30, "Large", "Small")) %>% 
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, area, size_group) %>%
  summarise(cod_stomach_content = sum(value)) %>% 
  arrange(name, year, area, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, area, sep = "_")) %>% 
  group_by(id, size_group) %>% # Add size-group here
  mutate(cod_stomach_content_tot = sum(cod_stomach_content),
         cod_stomach_content_prop = cod_stomach_content
         / cod_stomach_content_tot) %>% 
  ungroup()

# This should amount to the number of unique prey
cod_prey_long2 %>% group_by(id, size_group) %>% mutate(n = n()) %>% ungroup() %>% distinct(n)

# Split by size-group
cod_prey_long_small <- cod_prey_long2 %>% filter(size_group == "Small") %>%
  rename("cod_stomach_content_prop_small" = "cod_stomach_content_prop") %>%
  dplyr::select(name, id, cod_stomach_content_prop_small)

cod_prey_long_large <- cod_prey_long2 %>% filter(size_group == "Large") %>% 
  rename("cod_stomach_content_prop_large" = "cod_stomach_content_prop") %>%
  dplyr::select(name, id, cod_stomach_content_prop_large)

cod_prey_long_large %>% filter(cod_stomach_content_prop_large == "NaN")
cod_prey_long_small %>% filter(cod_stomach_content_prop_small == "NaN")
cod_prey_long_small <- cod_prey_long_small %>%
  mutate(cod_stomach_content_prop_small = ifelse(cod_stomach_content_prop_small == "NaN",
                                                 0,
                                                 cod_stomach_content_prop_small))

# Calculate Schoener index
schoener2 <- fle_prey_long %>%
  left_join(cod_prey_long_small) %>% 
  left_join(cod_prey_long_large) %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  drop_na(cod_stomach_content_prop_small) %>%
  drop_na(cod_stomach_content_prop_large) %>% 
  group_by(year, quarter, area) %>%
  summarise(schoener_f_sc = 1 - 0.5*(sum(abs(fle_stomach_content_prop - cod_stomach_content_prop_small))),
            schoener_f_lc = 1 - 0.5*(sum(abs(fle_stomach_content_prop - cod_stomach_content_prop_large))),
            schoener_sc_lc = 1 - 0.5*(sum(abs(cod_stomach_content_prop_small - cod_stomach_content_prop_large)))) %>% 
  ungroup()

schoener_long2 <- schoener2 %>% pivot_longer(4:6, names_to = "schoener_combination")

ggplot(schoener_long2, aes(schoener_combination, value, fill = factor(schoener_combination),
                           color = factor(schoener_combination))) +
  ggdist::stat_halfeye(adjust = 0.5, justification = -0.1, .width = 0, point_colour = NA, alpha = 0.8,
                       show.legend = FALSE) +
  geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5, show.legend = FALSE) +
  ggdist::stat_dots(side = "left", justification = 1.1, alpha = 0.8) + 
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2", name = "",
                    labels = c("Flounder-Cod (L)", "Flounder-Cod (S)", "Cod (S)-Cod (L)")) + 
  guides(color = FALSE, fill = guide_legend(override.aes = list(
    shape = 21, size = 2, fill = brewer.pal(n = 3, name = "Dark2"), color = brewer.pal(n = 3, name = "Dark2")))) +
  coord_flip() + 
  labs(y = "Value", x = "") +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.y = element_blank()) +
  ggtitle("Schoeners's overlap index") + 
  NULL

ggsave("figures/schoener_size_groups_data.png", width = 6.5, height = 6.5, dpi = 600)

# Prepare for analysis
schoener_long2 <- schoener_long2 %>%
  mutate(value2 = ifelse(value == 0, 0.0001, value),
         value2 = ifelse(value == 1, 1-0.0001, value2),
         year_f = as.factor(year),
         quarter_f = as.factor(quarter),
         area_f = as.factor(area),
         schoener_combination_f = as.factor(schoener_combination))
```

### Calculate Levins's index per 5 cm length groups!

```{r TEST: levin per size}
# This is just very exploratory...

fle_prey_long3 <- fle_prey %>%
  mutate(size_class = cut(pred_cm, breaks = c(seq(0, 100, 5)))) %>% 
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, area, size_class) %>%
  summarise(fle_stomach_content = sum(value)) %>% 
  arrange(name, size_class, year, area, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, area, size_class, sep = "_")) %>% 
  group_by(id) %>%
  mutate(fle_stomach_content_tot = sum(fle_stomach_content),
         fle_stomach_content_prop = fle_stomach_content / fle_stomach_content_tot) %>% 
  ungroup()

# Now cod
cod_prey_long3 <- cod_prey %>%
  mutate(size_class = cut(pred_cm, breaks = c(seq(0, 100, 5)))) %>% 
  pivot_longer(15:30) %>% 
  group_by(name, year, quarter, area, size_class) %>%
  summarise(cod_stomach_content = sum(value)) %>% 
  arrange(name, size_class, year, area, quarter) %>%
  ungroup() %>% 
  mutate(id = paste(year, quarter, area, size_class, sep = "_")) %>% 
  group_by(id) %>%
  mutate(cod_stomach_content_tot = sum(cod_stomach_content),
         cod_stomach_content_prop = cod_stomach_content / cod_stomach_content_tot) %>% 
  ungroup()

# Size based Levin's index
levin_cod <- cod_prey_long3 %>% 
  drop_na(name) %>% 
  drop_na(cod_stomach_content_prop) %>% 
  group_by(id, year, quarter, area, size_class) %>% 
  summarise(levin = ((1/(number_of_prey$n-1)) * (((1/sum(cod_stomach_content_prop^2))) - 1))) %>% 
  ungroup() %>% 
  mutate(size = as.integer(stringr::str_extract(size_class, "\\d+")))

levin_fle <- fle_prey_long3 %>% 
  drop_na(name) %>% 
  drop_na(fle_stomach_content_prop) %>% 
  group_by(id, year, quarter, area, size_class) %>% 
  summarise(levin = ((1/(number_of_prey$n-1)) * (((1/sum(fle_stomach_content_prop^2))) - 1))) %>% 
  ungroup() %>% 
  mutate(size = as.integer(stringr::str_extract(size_class, "\\d+")))

ggplot(levin_cod, aes(size, size_class)) + geom_point()

# Plot Levin
p1 <- levin_cod %>% filter(size > 5 & size < 60) %>% 
  ggplot(., aes(size, levin)) +
  geom_point() +
  stat_smooth() + 
  facet_wrap(~ area, scales = "free", ncol = 1) + 
  ggtitle("Cod")
  
p2 <- levin_fle %>% filter(size > 5 & size < 40) %>% 
  ggplot(., aes(size, levin)) +
  geom_point() +
  stat_smooth() + 
  facet_wrap(~ area, scales = "free", ncol = 1) +
  ggtitle("Fle")

p1 + p2

# How can I know this is not simply due to samples size? (more samples, more diversity)
# Plot n prey in individual stomachs vs sample size in the year, quarter, ices_rect and size_class
# If there's a strong positive relationship, larger mean number of preys 
saturation_fle_prey <- fle_prey %>%
  mutate(size_class = cut(pred_cm, breaks = c(seq(0, 100, 5)))) %>% 
  pivot_longer(15:30) %>% 
  filter(value > 0) %>% 
  group_by(unique_pred_id, year, quarter, area, size_class) %>%
  summarise(n_prey = n()) %>% 
  ungroup() %>% 
  group_by(year, quarter, area, size_class) %>%
  summarise(mean_n_prey = mean(n_prey), 
            sample_size_n = n()) %>% 
  ungroup()

ggplot(saturation_fle_prey, aes(sample_size_n, mean_n_prey, color = area)) +
  geom_jitter(alpha = 0.8, size = 2) +
  stat_smooth(method = "lm", se = FALSE) + 
  facet_wrap(~ size_class, scales = "free") + 
  scale_color_viridis(discrete = TRUE)

saturation_cod_prey <- cod_prey %>%
  mutate(size_class = cut(pred_cm, breaks = c(seq(0, 100, 5)))) %>% 
  pivot_longer(15:30) %>% 
  filter(value > 0) %>% 
  group_by(unique_pred_id, year, quarter, area, size_class) %>%
  summarise(n_prey = n()) %>% 
  ungroup() %>% 
  group_by(year, quarter, area, size_class) %>%
  summarise(mean_n_prey = mean(n_prey), 
            sample_size_n = n()) %>% 
  ungroup()

saturation_cod_prey %>% 
  mutate(size = as.integer(stringr::str_extract(size_class, "\\d+"))) %>% 
  ggplot(., aes(size, mean_n_prey)) +
  geom_point() + 
  stat_smooth()

ggplot(saturation_cod_prey, aes(sample_size_n, mean_n_prey, color = area)) +
  geom_jitter(alpha = 0.8) +
  facet_wrap(~ size_class, scales = "free") + 
  stat_smooth(method = "lm", se = FALSE) + 
  scale_color_viridis(discrete = TRUE) +
  guides(color = FALSE)
```
