---
title: "Cod diet: spatial analysis of cod and flounder diets in relation to density"
author: "Max Lindmark & Michele Casini"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Fit density (also referred to as CPUE) model with environmental predictors and use that to calculate weighted mean dissolved oxygen, temperature and depth of Baltic cod

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse); theme_set(theme_classic(base_size = 10))
library(readxl)
library(tidylog)
library(RCurl)
library(viridis)
library(RColorBrewer)
library(patchwork)
library(janitor)
library(icesDatras)
library(mapdata)
library(patchwork)
library(rgdal)
library(raster)
library(sf)
library(rgeos)
library(chron)
library(lattice)
library(ncdf4)
library(marmap)
library(rnaturalearth)
library(rnaturalearthdata)
library(mapplots)
library(EnvStats)
library(qwraps2)
#remotes::install_github("pbs-assess/sdmTMB")
library(sdmTMB)# To load entire cache in interactive r session, do: qwraps2::lazyload_cache_dir(path = "R/analysis/cod_flounder_diets_spatial_cache/html")
```

## For maps

```{r read coastline data, message=FALSE, warning=FALSE}
# Specify map ranges
ymin = 55; ymax = 58; xmin = 14; xmax = 20

map_data <- rnaturalearth::ne_countries(
  scale = "medium",
  returnclass = "sf", continent = "europe")

# Crop the polygon for plotting and efficiency:
# st_bbox(map_data) # find the rough coordinates
swe_coast <- suppressWarnings(suppressMessages(
  st_crop(map_data,
          c(xmin = xmin, ymin = ymin, xmax = xmax, ymax = ymax))))

# Transform our map into UTM 33 coordinates, which is the equal-area projection we fit in:
utm_zone33 <- 32633
swe_coast_proj <- sf::st_transform(swe_coast, crs = utm_zone33)

ggplot(swe_coast_proj) + geom_sf() 

# Define plotting theme for main plot
theme_plot <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
      axis.text.x = element_text(angle = 90),
      axis.text = element_text(size = 8),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 8),
      legend.position = "bottom",
      legend.key.height = unit(0.2, "cm"),
      legend.margin = margin(0, 0, 0, 0),
      legend.box.margin = margin(-5, -5, -5, -5),
      strip.text = element_text(size = 8, colour = 'black', margin = margin()),
      strip.background = element_rect(fill = "grey90")
      )
}

# Define plotting theme for facet_wrap map with years
theme_facet_map <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
        axis.text.x = element_text(angle = 90),
        axis.text = element_text(size = 6),
        strip.text = element_text(size = 8, colour = 'black', margin = margin()),
        strip.background = element_rect(fill = "grey90")
      )
}

# Make default base map plot
plot_map_raster <- 
ggplot(swe_coast_proj) + 
  geom_sf(size = 0.3) +
  labs(x = "Longitude", y = "Latitude") +
  theme_facet_map(base_size = 14)

# Function to convert from lat lon to UTM
LongLatToUTM <- function(x, y, zone){
  xy <- data.frame(ID = 1:length(x), X = x, Y = y)
  coordinates(xy) <- c("X", "Y")
  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
  return(as.data.frame(res))
}
```

## Read and plot data

```{r read and plot data}
cod <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/cod_diet_analysis.csv") %>% dplyr::select(-X1)

cod <- cod %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(year > 2014)

fle <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/fle_diet_analysis.csv") %>% dplyr::select(-X1)

fle <- fle %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth))
```

## Fit sdmTMB models with densities as covariates to stomach content data

```{r make meshes, cache=TRUE}
# Cod 
pcod_spde <- make_mesh(cod, c("X", "Y"), n_knots = 150, type = "kmeans", seed = 42)
plot(pcod_spde)

pfle_spde <- make_mesh(fle, c("X", "Y"), n_knots = 70, type = "kmeans", seed = 42)
plot(pfle_spde)
```

## Fit models of total content

```{r model total stomach content, cache=TRUE}
# Model total prey biomass 
# Cod
mcod <- sdmTMB(
  data = cod, 
  formula = tot_prey_biom_per_mass ~ 0 + quarter + as.factor(year) + predfle_density_sc*depth_sc + predcod_density_sc,
  time = "year", fields = "IID", spatial_only = FALSE, spde = pcod_spde, family = tweedie())

tidy(mcod)
summary(mcod)

cod$resids_mcod <- residuals(mcod) # randomized quantile residuals
qqnorm(cod$resids_mcod); abline(a = 0, b = 1)

# Flounder
mfle <- sdmTMB(
  data = fle, 
  formula = tot_prey_biom_per_mass ~ 0 + as.factor(year) + predfle_density_sc + predcod_density_sc*depth_sc,
  time = "year", fields = "IID", spatial_only = FALSE, spde = pfle_spde, family = tweedie())

tidy(mfle)
summary(mfle)

fle$resids_mfle <- residuals(mfle) # randomized quantile residuals
qqnorm(fle$resids_mfle); abline(a = 0, b = 1)
```

## Fit models of saduria content

```{r model saduria biomass in stomach, cache=TRUE}
# Model Saduria contents 
# Cod
mcodsad <- sdmTMB(
  data = cod, 
  formula = saduria_entomon_per_mass ~ 0 + quarter + as.factor(year) + predfle_density_sc*depth_sc + predcod_density_sc,
  time = "year", fields = "IID", spatial_only = FALSE, spde = pcod_spde, family = tweedie())

tidy(mcodsad)
summary(mcodsad)

cod$resids_mcodsad <- residuals(mcodsad) # randomized quantile residuals
qqnorm(cod$resids_mcodsad); abline(a = 0, b = 1)

# Flounder
mflesad <- sdmTMB(
  data = fle, 
  formula = saduria_entomon_per_mass ~ 0 + as.factor(year) + predfle_density_sc + predcod_density_sc*depth_sc,
  time = "year", fields = "IID", spatial_only = FALSE, spde = pfle_spde, family = tweedie())

tidy(mflesad)
summary(mflesad)

fle$resids_mflesad <- residuals(mflesad) # randomized quantile residuals
qqnorm(fle$resids_mflesad); abline(a = 0, b = 1)
```

## Calculate and plot marginal effects
#### Cod

```{r calculate marginal effects for cod models}
# Flounder density
nd_cod_fle <- data.frame(predfle_density_sc = seq(min(cod$predfle_density_sc),
                                                  max(cod$predfle_density_sc), length.out = 100))

nd_cod_fle$year <- 2018L
nd_cod_fle$predcod_density_sc <- 0
nd_cod_fle$depth_sc <- 0
nd_cod_fle$quarter <- factor(1)

sad_pred_cod_fle <- predict(mcodsad, newdata = nd_cod_fle, se_fit = TRUE, re_form = NA)
tot_pred_cod_fle <- predict(mcod, newdata = nd_cod_fle, se_fit = TRUE, re_form = NA)


# Cod density
nd_cod_cod <- data.frame(predcod_density_sc = seq(min(cod$predcod_density_sc),
                                                  max(cod$predcod_density_sc), length.out = 100))

nd_cod_cod$year <- 2018L
nd_cod_cod$predfle_density_sc <- 0
nd_cod_cod$depth_sc <- 0
nd_cod_cod$quarter <- factor(1)

sad_pred_cod_cod <- predict(mcodsad, newdata = nd_cod_cod, se_fit = TRUE, re_form = NA)
tot_pred_cod_cod <- predict(mcod, newdata = nd_cod_cod, se_fit = TRUE, re_form = NA)
```

#### Flounder

```{r calculate marginal effects for flounder models}
# Flounder density
nd_fle_fle <- data.frame(predfle_density_sc = seq(min(fle$predfle_density_sc),
                                                  max(fle$predfle_density_sc), length.out = 100))

nd_fle_fle$year <- 2018L
nd_fle_fle$predcod_density_sc <- 0
nd_fle_fle$depth_sc <- 0

sad_pred_fle_fle <- predict(mflesad, newdata = nd_fle_fle, se_fit = TRUE, re_form = NA)
tot_pred_fle_fle <- predict(mfle, newdata = nd_fle_fle, se_fit = TRUE, re_form = NA)

# Cod density
nd_fle_cod <- data.frame(predcod_density_sc = seq(min(fle$predcod_density_sc),
                                                  max(fle$predcod_density_sc), length.out = 100))

nd_fle_cod$year <- 2018L
nd_fle_cod$predfle_density_sc <- 0
nd_fle_cod$depth_sc <- 0

sad_pred_fle_cod <- predict(mflesad, newdata = nd_fle_cod, se_fit = TRUE, re_form = NA)
tot_pred_fle_cod <- predict(mfle, newdata = nd_fle_cod, se_fit = TRUE, re_form = NA)
```

#### Plot marginal effects

```{r plot marginal effects}
# Saduria models
p1 <- ggplot(sad_pred_fle_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  coord_cartesian(ylim = c(0, 0.015), expand = 0) + 
  labs(y = "Saduria in flounder stomach [g/g]", x = "")

p2 <- ggplot(sad_pred_fle_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  coord_cartesian(ylim = c(0, 0.015), expand = 0) + 
  labs(y = "", x = "")

p3 <- ggplot(sad_pred_cod_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  labs(y = "Saduria in cod stomach [g/g]", x = "Scaled flounder density")

p4 <- ggplot(sad_pred_cod_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  labs(y = "", x = "Scaled cod density")

p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

ggsave("figures/marginal_effects_saduria.png", width = 6.5, height = 6.5, dpi = 600)

# Total stomach content models
p5 <- ggplot(tot_pred_fle_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  coord_cartesian(ylim = c(0, 0.033), expand = 0) + 
  labs(y = "Prey biomass in flounder stomach [g/g]", x = "")

p6 <- ggplot(tot_pred_fle_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  coord_cartesian(ylim = c(0, 0.033), expand = 0) + 
  labs(y = "", x = "")

p7 <- ggplot(tot_pred_cod_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  coord_cartesian(ylim = c(0, 0.028), expand = 0) + 
  labs(y = "Prey biomass in cod stomach [g/g]", x = "Scaled flounder density")

p8 <- ggplot(tot_pred_cod_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  coord_cartesian(ylim = c(0, 0.028), expand = 0) + 
  labs(y = "", x = "Scaled cod density")

p5 + p6 + p7 + p8 + plot_layout(ncol = 2)

ggsave("figures/marginal_effects_total.png", width = 6.5, height = 6.5, dpi = 600)
```

## No do the same for total stomach contents

```{r plot marginal effects for full stomach content}
## Flounder
# Flounder density
nd_fle_fle <- data.frame(predfle_density_sc = seq(min(fle$predfle_density_sc),
                                                  max(fle$predfle_density_sc), length.out = 100))

nd_fle_fle$year <- 2018L
nd_fle_fle$predcod_density_sc <- 0
nd_fle_fle$depth_sc <- 0

pred_fle_fle <- predict(mflesad, newdata = nd_fle_fle, se_fit = TRUE, re_form = NA)

p1 <- ggplot(pred_fle_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  coord_cartesian(ylim = c(0, 0.015), expand = 0) + 
  labs(y = "Saduria in stomach [g/g]", x = "")

# Cod density
nd_fle_cod <- data.frame(predcod_density_sc = seq(min(fle$predcod_density_sc),
                                                  max(fle$predcod_density_sc), length.out = 100))

nd_fle_cod$year <- 2018L
nd_fle_cod$predfle_density_sc <- 0
nd_fle_cod$depth_sc <- 0

pred_fle_cod <- predict(mflesad, newdata = nd_fle_cod, se_fit = TRUE, re_form = NA)

p2 <- ggplot(pred_fle_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  coord_cartesian(ylim = c(0, 0.015), expand = 0) + 
  labs(y = "", x = "")

flemargin <- p1 + p2 + plot_annotation(title = "",
                                       theme = theme(plot.title = element_text(size = 16, hjust = 0.5)))

## Cod
# Flounder density
nd_cod_fle <- data.frame(predfle_density_sc = seq(min(cod$predfle_density_sc),
                                                  max(cod$predfle_density_sc), length.out = 100))

nd_cod_fle$year <- 2018L
nd_cod_fle$predcod_density_sc <- 0
nd_cod_fle$depth_sc <- 0
nd_cod_fle$quarter <- factor(1)

pred_cod_fle <- predict(mcodsad, newdata = nd_cod_fle, se_fit = TRUE, re_form = NA)

p3 <- ggplot(pred_cod_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  labs(y = "Saduria in stomach [g/g]", x = "Scaled flounder density")

# Cod density
nd_cod_cod <- data.frame(predcod_density_sc = seq(min(cod$predcod_density_sc),
                                                  max(cod$predcod_density_sc), length.out = 100))

nd_cod_cod$year <- 2018L
nd_cod_cod$predfle_density_sc <- 0
nd_cod_cod$depth_sc <- 0
nd_cod_cod$quarter <- factor(1)

pred_cod_cod <- predict(mcodsad, newdata = nd_cod_cod, se_fit = TRUE, re_form = NA)

p4 <- ggplot(pred_cod_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  labs(y = "", x = "Scaled cod density")

codmargin <- p3 + p4 + plot_annotation(title = "Cod marginal effects",
                                       theme = theme(plot.title = element_text(size = 16, hjust = 0.5)))

flemargin / codmargin # Add silhouettes here?

ggsave("figures/margina_saduria.png", width = 6.5, height = 6.5, dpi = 600)
```

```{r}
knitr::knit_exit()
```
