---
title: "Cod diet: spatial analysis of cod and flounder stomach content in relation to density"
author: "Max Lindmark & Michele Casini"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Spatial analysis of cod and flounder stomach content in relation to density using `sdmTMB`

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse); theme_set(theme_light(base_size = 12))
library(readxl)
library(tidylog)
library(RCurl)
library(viridis)
library(RColorBrewer)
library(patchwork)
library(janitor)
library(icesDatras)
library(mapdata)
library(patchwork)
library(rgdal)
library(raster)
library(sf)
library(rgeos)
library(chron)
library(lattice)
library(ncdf4)
library(marmap)
library(rnaturalearth)
library(rnaturalearthdata)
library(mapplots)
library(EnvStats)
library(qwraps2)
#remotes::install_github("pbs-assess/sdmTMB")
library(sdmTMB)

# To load entire cache in interactive r session, do:
# qwraps2::lazyload_cache_dir(path = "R/analysis/stomach_fullness_spatial_cache/html")
```

## For maps

```{r read coastline data, message=FALSE, warning=FALSE}
# Specify map ranges
ymin = 55; ymax = 58; xmin = 14; xmax = 20

map_data <- rnaturalearth::ne_countries(
  scale = "medium",
  returnclass = "sf", continent = "europe")

# Crop the polygon for plotting and efficiency:
# st_bbox(map_data) # find the rough coordinates
swe_coast <- suppressWarnings(suppressMessages(
  st_crop(map_data,
          c(xmin = xmin, ymin = ymin, xmax = xmax, ymax = ymax))))

# Transform our map into UTM 33 coordinates, which is the equal-area projection we fit in:
utm_zone33 <- 32633
swe_coast_proj <- sf::st_transform(swe_coast, crs = utm_zone33)

ggplot(swe_coast_proj) + geom_sf() 

# Define plotting theme for main plot
theme_plot <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
      axis.text.x = element_text(angle = 90),
      axis.text = element_text(size = 8),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 8),
      legend.position = "bottom",
      legend.key.height = unit(0.2, "cm"),
      legend.margin = margin(0, 0, 0, 0),
      legend.box.margin = margin(-5, -5, -5, -5),
      strip.text = element_text(size = 8, colour = 'black', margin = margin()),
      strip.background = element_rect(fill = "grey90")
      )
}

# Define plotting theme for facet_wrap map with years
theme_facet_map <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
        axis.text.x = element_text(angle = 90),
        axis.text = element_text(size = 6),
        strip.text = element_text(size = 8, colour = 'black', margin = margin()),
        strip.background = element_rect(fill = "grey90")
      )
}

# Make default base map plot
plot_map_raster <- 
ggplot(swe_coast_proj) + 
  geom_sf(size = 0.3) +
  labs(x = "Longitude", y = "Latitude") +
  theme_facet_map(base_size = 14)

# Function to convert from lat lon to UTM
LongLatToUTM <- function(x, y, zone){
  xy <- data.frame(ID = 1:length(x), X = x, Y = y)
  coordinates(xy) <- c("X", "Y")
  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
  return(as.data.frame(res))
}

theme_clean <- function() {
  theme_minimal(base_family = "Barlow Semi Condensed") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "BarlowSemiCondensed-Bold"),
          axis.title = element_text(family = "BarlowSemiCondensed-Medium"),
          strip.text = element_text(family = "BarlowSemiCondensed-Bold",
                                    size = rel(1), hjust = 0),
          strip.background = element_rect(fill = "grey80", color = NA))
}
```

## Read and plot data

```{r read and plot data}
# These data are for total and prey specific stomach models
cod <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/cod_diet_analysis.csv") %>% dplyr::select(-X1)

cod <- cod %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(year > 2014) %>%
  filter(!quarter == 2) %>% 
  drop_na(predfle_density_sc, predcod_density_sc) %>% 
  droplevels()

fle <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_interactions/data/fle_diet_analysis.csv") %>% dplyr::select(-X1)

fle <- fle %>%
  mutate(year = as.integer(year),
         quarter = as.factor(quarter),
         depth2_sc = depth - mean(depth),
         saduria_entomon_per_mass = saduria_entomon_tot/pred_weight_g,
         tot_prey_biom_per_mass = tot_prey_biom/pred_weight_g,
         depth_sc = (depth - mean(depth)) / sd(depth)) %>% 
  filter(!quarter == 2) %>% 
  drop_na(predfle_density_sc, predcod_density_sc) %>% 
  droplevels()

# Plot data (with smoother)
ggplot(fle, aes(predfle_density_sc, tot_prey_biom_per_mass)) +
    geom_point() +
    stat_smooth(method = "gam", formula = y ~ s(x, k = 3))
  
ggplot(fle, aes(predcod_density_sc, tot_prey_biom_per_mass)) +
  geom_point() +
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3))

ggplot(cod, aes(predfle_density_sc, tot_prey_biom_per_mass)) +
    geom_point() +
    stat_smooth(method = "gam", formula = y ~ s(x, k = 3))
  
ggplot(cod, aes(predcod_density_sc, tot_prey_biom_per_mass)) +
  geom_point() +
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3))
```

## Read the prediction grids

```{r read and process prediction grid, message=FALSE, warning=FALSE}
# And now read in pred_grid2 which has oxygen values at location and time and depth:
pred_grid2 <- readr::read_csv("https://raw.githubusercontent.com/maxlindmark/cod_interactions/main/data/pred_grid2.csv")

# Clean
pred_grid2 <- pred_grid2 %>%
  mutate(year = as.integer(year)) %>% 
  drop_na(depth)

# Add ices_rect
pred_grid2$ices_rect <- ices.rect2(pred_grid2$lon, pred_grid2$lat) 
```

## Fit `sdmTMB` models with densities as covariates to stomach content data. First make mesh

```{r make meshes}
# Cod 
pcod_spde <- make_mesh(cod, c("X", "Y"), n_knots = 150, type = "kmeans", seed = 42)
plot(pcod_spde)

pfle_spde <- make_mesh(fle, c("X", "Y"), n_knots = 70, type = "kmeans", seed = 42)
plot(pfle_spde)
```

## Fit models of total content
** first maybe fit beta models of these prey types they have in common over size, because saduria is not eaten by larger cod anymore. Though, cpue is not by size... hmm, might have to change that!

```{r model total stomach content, cache=TRUE}
# Model total prey biomass 
# Cod 
mcod <- sdmTMB(
  data = cod, 
  formula = tot_prey_biom_per_mass ~ 0 + quarter + as.factor(year) + predfle_density_sc + predcod_density_sc,
  time = "year", spatiotemporal = "IID", spatial = "on", mesh = pcod_spde, family = tweedie())

tidy(mcod)
summary(mcod)

cod$resids_mcod <- residuals(mcod) # randomized quantile residuals
qqnorm(cod$resids_mcod); abline(a = 0, b = 1)

# Flounder
mfle <- sdmTMB(
  data = fle, 
  formula = tot_prey_biom_per_mass ~ 0 + quarter + as.factor(year) + predfle_density_sc + predcod_density_sc,
  time = "year", spatiotemporal = "IID", spatial = "on", mesh = pfle_spde, family = tweedie())

tidy(mfle)
summary(mfle)

fle$resids_mfle <- residuals(mfle) # randomized quantile residuals
qqnorm(fle$resids_mfle); abline(a = 0, b = 1)
```

## Fit models of saduria content

```{r model saduria biomass in stomach, cache=TRUE}
# Model Saduria contents 
# Cod
mcodsad <- sdmTMB(
  data = cod, 
  formula = saduria_entomon_per_mass ~ 0 + quarter + as.factor(year) + predfle_density_sc + predcod_density_sc,
  time = "year", spatiotemporal = "IID", spatial = "on", mesh = pcod_spde, family = tweedie())

tidy(mcodsad)
summary(mcodsad)

cod$resids_mcodsad <- residuals(mcodsad) # randomized quantile residuals
qqnorm(cod$resids_mcodsad); abline(a = 0, b = 1)

# Flounder
mflesad <- sdmTMB(
  data = fle, 
  formula = saduria_entomon_per_mass ~ 0 + quarter + as.factor(year) + predfle_density_sc + predcod_density_sc,
  time = "year", spatiotemporal = "IID", spatial = "on", mesh = pfle_spde, family = tweedie())

tidy(mflesad)
summary(mflesad)

fle$resids_mflesad <- residuals(mflesad) # randomized quantile residuals
qqnorm(fle$resids_mflesad); abline(a = 0, b = 1)
```

## Plot effect sizes

```{r}
mcod_ef <- tidy(mcod, effects = "fixed", conf.int = TRUE) %>%
  filter(term %in% c("predfle_density_sc", "predcod_density_sc")) %>% 
  mutate(species = "Cod", response = "Total prey")

mfle_ef <- tidy(mfle, effects = "fixed", conf.int = TRUE) %>%
  filter(term %in% c("predfle_density_sc", "predcod_density_sc")) %>% 
  mutate(species = "Flounder", response = "Total prey")

mcodsad_ef <- tidy(mcodsad, effects = "fixed", conf.int = TRUE) %>%
  filter(term %in% c("predfle_density_sc", "predcod_density_sc")) %>% 
  mutate(species = "Cod", response = "Saduria")

mflesad_ef <- tidy(mflesad, effects = "fixed", conf.int = TRUE) %>%
  filter(term %in% c("predfle_density_sc", "predcod_density_sc")) %>% 
  mutate(species = "Flounder", response = "Saduria")

plot_df <- bind_rows(mcod_ef, mfle_ef, mcodsad_ef, mflesad_ef) %>% 
  mutate(term = ifelse(term == "predcod_density_sc", "Cod density", "Flounder density"))

# Plot effects
plot_df %>% 
  ggplot(., aes(term, estimate, color = factor(species))) +
  geom_hline(yintercept = 0, linetype = 2, color = "gray50", size = 0.75) +
  geom_point(size = 3, position = position_dodge(width = 0.2)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2,
                position = position_dodge(width = 0.2), size = 1) +
  scale_color_brewer(palette = "Dark2", name = "Species") +
  labs(x = "Predictor", y = "Standardized coefficient") +
  theme_light(base_size = 12) + 
  facet_wrap(~response) +
  theme(legend.position = "bottom") +
  NULL 

ggsave("figures/stomach_content_effect_size.png", width = 6.5, height = 6.5, dpi = 600)
```

## Calculate and plot marginal effects
#### Cod

```{r calculate marginal effects for cod models}
# Flounder density
nd_cod_fle <- data.frame(predfle_density_sc = seq(min(cod$predfle_density_sc),
                                                  max(cod$predfle_density_sc), length.out = 100))

nd_cod_fle$year <- 2018L
nd_cod_fle$predcod_density_sc <- 0
nd_cod_fle$depth_sc <- 0
nd_cod_fle$quarter <- factor(4)

sad_pred_cod_fle <- predict(mcodsad, newdata = nd_cod_fle, se_fit = TRUE, re_form = NA)
tot_pred_cod_fle <- predict(mcod, newdata = nd_cod_fle, se_fit = TRUE, re_form = NA)

# Cod density
nd_cod_cod <- data.frame(predcod_density_sc = seq(min(cod$predcod_density_sc),
                                                  max(cod$predcod_density_sc), length.out = 100))

nd_cod_cod$year <- 2018L
nd_cod_cod$predfle_density_sc <- 0
nd_cod_cod$depth_sc <- 0
nd_cod_cod$quarter <- factor(4)

sad_pred_cod_cod <- predict(mcodsad, newdata = nd_cod_cod, se_fit = TRUE, re_form = NA)
tot_pred_cod_cod <- predict(mcod, newdata = nd_cod_cod, se_fit = TRUE, re_form = NA)
```

#### Flounder

```{r calculate marginal effects for flounder models}
# Flounder density
nd_fle_fle <- data.frame(predfle_density_sc = seq(min(fle$predfle_density_sc),
                                                  max(fle$predfle_density_sc), length.out = 100))

nd_fle_fle$year <- 2018L
nd_fle_fle$predcod_density_sc <- 0
nd_fle_fle$depth_sc <- 0
nd_fle_fle$quarter <- factor(4)

sad_pred_fle_fle <- predict(mflesad, newdata = nd_fle_fle, se_fit = TRUE, re_form = NA)
tot_pred_fle_fle <- predict(mfle, newdata = nd_fle_fle, se_fit = TRUE, re_form = NA)

# Cod density
nd_fle_cod <- data.frame(predcod_density_sc = seq(min(fle$predcod_density_sc),
                                                  max(fle$predcod_density_sc), length.out = 100))

nd_fle_cod$year <- 2018L
nd_fle_cod$predfle_density_sc <- 0
nd_fle_cod$depth_sc <- 0
nd_fle_cod$quarter <- factor(4)

sad_pred_fle_cod <- predict(mflesad, newdata = nd_fle_cod, se_fit = TRUE, re_form = NA)
tot_pred_fle_cod <- predict(mfle, newdata = nd_fle_cod, se_fit = TRUE, re_form = NA)
```

#### Plot marginal effects

```{r plot marginal effects}
# Saduria models
p1 <- ggplot(sad_pred_fle_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  labs(y = "Saduria in flounder stomach [g/g]", x = "")

p2 <- ggplot(sad_pred_fle_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  labs(y = "", x = "")

p3 <- ggplot(sad_pred_cod_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  labs(y = "Saduria in cod stomach [g/g]", x = "Scaled flounder density")

p4 <- ggplot(sad_pred_cod_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  labs(y = "", x = "Scaled cod density")

p1 + p2 + p3 + p4 + plot_layout(ncol = 2)

ggsave("figures/marginal_effects_saduria.png", width = 6.5, height = 6.5, dpi = 600)

# Total stomach content models
p5 <- ggplot(tot_pred_fle_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  labs(y = "Prey biomass in flounder stomach [g/g]", x = "")

p6 <- ggplot(tot_pred_fle_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  labs(y = "", x = "")

p7 <- ggplot(tot_pred_cod_fle, aes(predfle_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) +
  labs(y = "Prey biomass in cod stomach [g/g]", x = "Scaled flounder density")

p8 <- ggplot(tot_pred_cod_cod, aes(predcod_density_sc, exp(est),
  ymin = exp(est - 1.96 * est_se), ymax = exp(est + 1.96 * est_se))) +
  geom_line() + geom_ribbon(alpha = 0.4) + 
  labs(y = "", x = "Scaled cod density")

p5 + p6 + p7 + p8 + plot_layout(ncol = 2)

ggsave("figures/marginal_effects_total.png", width = 6.5, height = 6.5, dpi = 600)
```

```{r}
knitr::knit_exit()
```
