---
title: "Clean diet data for analysis"
author: "Max Lindmark & Michele Casini"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
  df_print: paged
pdf_document: default
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Intro
Calculate response (feeding ration, total weight of prey groups) and predictor variables for diet data, aggregate to get 1 stomach = 1 row

```{r lib, message=FALSE}
# Load libraries, install if needed
library(tidyverse); theme_set(theme_light(base_size = 10))
library(readxl)
library(tidylog)
library(RCurl)
library(viridis)
library(RColorBrewer)
library(patchwork)
library(janitor)
library(icesDatras)
library(mapdata)
library(patchwork)
library(rgdal)
library(raster)
library(sf)
library(rgeos)
library(chron)
library(lattice)
library(ncdf4)
library(marmap)
library(rnaturalearth)
library(rnaturalearthdata)
library(mapplots)
library(EnvStats)
library(qwraps2)
library(forcats)
#remotes::install_github("pbs-assess/sdmTMB")
library(sdmTMB)# To load entire cache in interactive r session, do: qwraps2::lazyload_cache_dir(path = "R/analysis/spatial_trend_models_cache/html")
```

## For maps

```{r read coastline data, message=FALSE, warning=FALSE}
# Specify map ranges
ymin = 55; ymax = 58; xmin = 14; xmax = 20

map_data <- rnaturalearth::ne_countries(
  scale = "medium",
  returnclass = "sf", continent = "europe")

# Crop the polygon for plotting and efficiency:
# st_bbox(map_data) # find the rough coordinates
swe_coast <- suppressWarnings(suppressMessages(
  st_crop(map_data,
          c(xmin = xmin, ymin = ymin, xmax = xmax, ymax = ymax))))

# Transform our map into UTM 33 coordinates, which is the equal-area projection we fit in:
utm_zone33 <- 32633
swe_coast_proj <- sf::st_transform(swe_coast, crs = utm_zone33)

ggplot(swe_coast_proj) + geom_sf() 

# Define plotting theme for main plot
theme_plot <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
      axis.text.x = element_text(angle = 90),
      axis.text = element_text(size = 8),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 8),
      legend.position = "bottom",
      legend.key.height = unit(0.2, "cm"),
      legend.margin = margin(0, 0, 0, 0),
      legend.box.margin = margin(-5, -5, -5, -5),
      strip.text = element_text(size = 8, colour = 'black', margin = margin()),
      strip.background = element_rect(fill = "grey90")
      )
}

# Define plotting theme for facet_wrap map with years
theme_facet_map <- function(base_size = 10, base_family = "") {
  theme_light(base_size = 10, base_family = "") +
    theme(
        axis.text.x = element_text(angle = 90),
        axis.text = element_text(size = 6),
        strip.text = element_text(size = 8, colour = 'black', margin = margin()),
        strip.background = element_rect(fill = "grey90")
      )
}

# Make default base map plot
plot_map_raster <- 
ggplot(swe_coast_proj) + 
  geom_sf(size = 0.3) +
  labs(x = "Longitude", y = "Latitude") +
  theme_facet_map(base_size = 14)

# Function to convert from lat lon to UTM
LongLatToUTM <- function(x, y, zone){
  xy <- data.frame(ID = 1:length(x), X = x, Y = y)
  coordinates(xy) <- c("X", "Y")
  proj4string(xy) <- CRS("+proj=longlat +datum=WGS84")  ## for example
  res <- spTransform(xy, CRS(paste("+proj=utm +zone=",zone," ellps=WGS84",sep='')))
  return(as.data.frame(res))
}
```

## Read data

```{r read data, warning=FALSE}
d <- readr::read_csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/bentfish/data/for_analysis/stomach/full_stomach_data_21.10.25.csv") %>% dplyr::select(-X1)

# Drop NA coordinates (because these do not even have ices-rectangle, see diet data processing script in benthfish project)
d <- d %>% drop_na(Long) %>% drop_na(Lat)

# Add UTM coordinates (first rename )
utm_coords <- LongLatToUTM(d$Long, d$Lat, zone = 33)
d$X <- utm_coords$X/1000
d$Y <- utm_coords$Y/1000
```

## Plot data

```{r plot data, warning=FALSE}
head(data.frame(d))
sort(colnames(d))
#  [1] "Age"                    "Comment"                "comments"               "Coun."                 
#  [5] "Cruise"                 "Date"                   "Day"                    "Depth.catch"           
#  [9] "Depthstep"              "Gall.content"           "Gonad.weight.roundfish" "HN"                    
# [13] "Ices.rect"              "Index"                  "Lat"                    "Length.code"           
# [17] "Liver.weight.roundfish" "Long"                   "Maturity"               "Month"                 
# [21] "N.empty"                "N.regurgitated"         "N.skeletal"             "N.with.food"           
# [25] "Number"                 "Parasites.in.stomach"   "Perc.stomac.content"    "Pred.size.mm"          
# [29] "Pred.weight.g"          "Predator.code"          "Predator.gutted.weight" "Prey.nr"               
# [33] "Prey.size"              "Prey.sp.code"           "Prey.weight"            "Processed"             
# [37] "Q.year"                 "Quarter"                "Sample"                 "Sample.type"           
# [41] "Sex"                    "Ship"                   "source"                 "Stage.digestion"       
# [45] "Stomach.content"        "SubDiv"                 "transect"               "Unique.pred.id"        
# [49] "X"

# Plot data in space, color by survey
plot_map_raster +
  geom_point(data = d, aes(x = X * 1000, y = Y * 1000, color = Cruise), size = 0.5) +
  scale_color_brewer(palette = "Set2") + 
  facet_wrap(~ Cruise, ncol = 3) + 
  theme_plot()
```

## Summarize and organize data

```{r summarize data}
# Calculate total weight of prey by predator ID and prey species (i.e., across prey sizes)
# Create wide data frame so that I can sum easily across prey groups (columns)
# I.e., one row = one stomach from here!
d_wide <- d %>% 
  drop_na(Prey.weight) %>% 
  group_by(Unique.pred.id, Prey.sp.code) %>% 
  summarise(tot_biom_per_prey = sum(Prey.weight)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = Prey.sp.code, values_from = tot_biom_per_prey) %>% 
  mutate(across(everything(), ~replace_na(.x, 0))) %>% # Replace NA with 0, because it means the prey does not exist
  janitor::clean_names()

head(d_wide)
str(d_wide)
colnames(d_wide)
 
# Now make some calculations and aggregate some taxonomic level. Since all columns are assigned to 
# some higher level group (or the same group), the sum of these is the total stomach content. 
# Note that I have one group for unidentified clupeids, but also sprat and herring. So if I want the 
# total of some aggregated group, then I need to add all the sub-groups.

# CHECK all these are covered now that I also use old stomach data!

d_wide2 <- d_wide %>% 
  mutate(amphipoda_tot = hyperia_galba + gammarus_sp + monoporeia_affinis + 
           corophium_volutator + amphipoda,
         bivalvia_tot = bivalvia + mytilus_sp + cerastoderma_glaucum + mya_arenaria + macoma_balthica + 
           mytilus_edulis + limecola_balthica,
         clupeidae_tot = clupeidae + clupeidae_2,
         clupea_harengus_tot = clupea_harengus + clupea_harengus_2,
         gadus_morhua_tot = gadus_morhua,
         gadiformes_tot = gadidae + merlangius_merlangus,
         gobiidae_tot = gobiidae,
         mysidae_tot = mysis_relicta + mysidae + neomysis_integer + mysis_mixta + mysida + gastrosacus,
         non_bio_tot = stone + plastic + sand + wood + litter + carbon + stone_2 + carbon_2 + wood_2 + 
           litter_plastics + sand_2,
         other_crustacea_tot = pontoporeia_femorata + crangon_crangon + idotea_balthica + cumacea + 
           praunus_flexuosus + crustacea + diastylis_rathkei + palaemon_sp + palaemon_elegans + caridea +
           amphibalanus_improvisus + palaemonidae + carcinus_maenas + copepoda + calanoida + pontoporeiidae + decapoda, 
         other_tot = halicryptus_spinulosus + priapulus_caudatus + annelida + algae + priapulidae + waste +
           unidentified_mass + spine + empty + mollusca + na + remains + gastropoda + hydrobia_sp + 
           priapulida + halicryptus + digestive_tract + mucus + remains_2 + pontoporeidae + pontoporeia_sp + 
           halicryptus_spinolusus + priapulida_2 + prapulida,
         other_pisces_tot = pomatoschistus_minutus + pisces + pisces_eggs + enchelyopus_cimbrius + trachurus_trachurus +
           gasterosteus_aculeatus + scales + pleuronectes_platessa + anguilla_anguilla + pungitius_pungitius + ammodytes_tobianus +
           cottidae + spinachia_spinachia + zoarces_viviparus + ammodytidae + myoxocephalus_quadricornis +
           hyperoplus_lanceolatus + pleuronectiformes + scophthalmus_maximus + neogobius_melanostomus + gobius_niger +
           pleuronectidae + gasterosteidae + belone_belone + agonus_cataphractus + myoxocephalus_scorpius,
         platichthys_flesus_tot = platichthys_flesus,
         polychaeta_tot = bylgides_sarsi + scoloplos_armiger + terebellides_stroemii + hediste_diversicolor + 
           phyllodocida + polychaeta + pectinaria_sp + nephtys_ciliata,
         saduria_entomon_tot = saduria_entomon,
         sprattus_sprattus_tot = sprattus_sprattus + sprattus_sprattus_2
         )

# 16 prey groups in total

length(unique(d$Unique.pred.id))
nrow(d_wide2) # The reason they differ in length (nrow) is because I remove NA prey weight
length(unique(drop_na(d, Prey.weight)$Unique.pred.id))

# Select only columns aggregated columns (ending with _tot)
data.frame(d_wide2[1, c(1, 118:133)])
d_wide3 <- d_wide2 %>% dplyr::select(c(1, 118:133))

sort(colnames(d_wide3))

# Add back in other information 
d_sub <- d %>%
  dplyr::select(Year, Quarter, Cruise, HN, Sample, Predator.code, X, Y, Lat, Long, Ices.rect,
                Pred.size.mm, Pred.weight.g, Unique.pred.id, source) %>% 
  rename("Predator.spec" = "Predator.code") %>% 
  distinct(Unique.pred.id, .keep_all = TRUE) %>%
  janitor::clean_names()  

d_wide4 <- left_join(d_wide3, d_sub) # Why missing 1,121 IDs? I lose them when making d_wide, I filter non-NA prey weights!
# missing_ids <- unique(d_sub$unique_pred_id)[!unique(d_sub$unique_pred_id) %in% unique(d_wide3$unique_pred_id)]
# d %>% filter(Unique.pred.id %in% missing_ids) %>% distinct(Prey.weight)

colnames(d_wide4)
data.frame(d_wide4[1, 2:17])
d_wide4 <- d_wide4 %>% mutate(tot_prey_biom = rowSums(.[2:17]))

d_wide4 %>% group_by(unique_pred_id) %>% mutate(n = n()) %>% ungroup() %>% distinct(n)

# Split data by species
fle <- d_wide4 %>%
  filter(predator_spec == "FLE") %>% 
  mutate(pred_cm = pred_size_mm/10,
         pred_cm_class = cut(pred_cm, breaks = c(0, 9, 20, 30, 200), right = TRUE))

head(data.frame(fle), 20)
unique(fle$pred_cm_class)

cod <- d_wide4 %>%
  filter(predator_spec == "COD") %>% 
  mutate(pred_cm = pred_size_mm/10,
         pred_cm_class = cut(pred_cm, breaks = c(0, 6, 20, 30, 40, 50, 200), right = TRUE))

head(data.frame(cod), 20)
unique(cod$pred_cm_class)
```

## Find which prey are shared for cod and flounder and explore data more

```{r plot potential response variables}
# First subset data to new and old (years with flounder data and without)
# Plot and calculate proportion empty stomachs
cod %>% 
  mutate(empty_stomach = ifelse(tot_prey_biom == 0, "Y", "N")) %>% 
  ggplot(., aes(empty_stomach, fill = empty_stomach)) + 
  scale_fill_brewer(palette = "Set2") +
  geom_bar()

# Plot "stomach" fullness, i.e., the weight of prey in stomach (relative to predator weight)
# Can also be called Feeding Ratio, FR
t <- cod %>% drop_na(pred_weight_g)
t <- cod %>% drop_na(pred_cm)

# Next find the most abundance prey groups for cod and flounder (to see if the density has any effect
# on the biomass of common prey in their stomachs)
# To do that, I need long format again, group by prey item and summarize
colnames(cod)
cod_important_prey <- cod %>%
  filter(year > 2014) %>% # Compare only recent data!
  pivot_longer(2:17) %>% 
  group_by(name) %>% 
  summarise(tot_prey = sum(value)) %>% 
  mutate(percent = round(tot_prey / sum(tot_prey), digits = 5)*100) %>%  # calculate also percent of total
  arrange(desc(tot_prey)) %>% 
  mutate(spec = "cod")

# Same for flounder
fle_important_prey <- fle %>%
  pivot_longer(2:17) %>% 
  group_by(name) %>% 
  summarise(tot_prey = sum(value)) %>% 
  mutate(percent = round(tot_prey / sum(tot_prey), digits = 2)*100) %>%  # calculate also percent of total
  arrange(desc(tot_prey)) %>% 
  mutate(spec = "fle")

plotdat <- bind_rows(cod_important_prey, fle_important_prey) %>% filter(percent > 0)

ggplot(plotdat, aes(reorder(name, desc(percent)), percent, fill = spec)) +
  geom_bar(stat = "identity") + 
  theme_classic(base_size = 16) + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_fill_brewer(palette = "Set2") + 
  NULL

# Ok, so the species that both prey feed on (even though very little(!)) are:
plotdat %>% arrange(desc(percent)) %>% as.data.frame()
```

Calculate response variables

```{r calculate summaries and response variables}
# Total feeding ratio, proportion of saduria and proportion of common prey!
# Cod
cod <- cod %>% 
  mutate(pred_weight_g = replace_na(pred_weight_g, -9),
         pred_weight_g = ifelse(pred_weight_g == -9, 0.01*pred_cm^3, pred_weight_g), 
         FR_tot = (tot_prey_biom)/(pred_weight_g - tot_prey_biom),
         FR_sad = (saduria_entomon_tot)/(pred_weight_g - tot_prey_biom), # important I remove tot prey here!
         FR_spr = (sprattus_sprattus_tot)/(pred_weight_g - tot_prey_biom), # important I remove tot prey here!
         prop_saduria = saduria_entomon_tot/tot_prey_biom,
         prop_common = (amphipoda_tot + clupea_harengus_tot + clupeidae_tot + other_crustacea_tot + 
                          other_pisces_tot + polychaeta_tot + saduria_entomon_tot + sprattus_sprattus_tot) / tot_prey_biom,
         common_tot = (amphipoda_tot + clupea_harengus_tot + clupeidae_tot + other_crustacea_tot +
                        other_pisces_tot + polychaeta_tot + saduria_entomon_tot + sprattus_sprattus_tot)) %>% 
  filter(FR_tot > -1) # remove negative values of FR

# Flounder  
fle <- fle %>% 
  mutate(pred_weight_g = replace_na(pred_weight_g, -9),
         pred_weight_g = ifelse(pred_weight_g == -9, 0.01*pred_cm^3, pred_weight_g), 
         FR_tot = (tot_prey_biom)/(pred_weight_g - tot_prey_biom), 
         FR_sad = (saduria_entomon_tot)/(pred_weight_g - tot_prey_biom), # important I remove tot prey here!
         FR_spr = (sprattus_sprattus_tot)/(pred_weight_g - tot_prey_biom), # important I remove tot prey here!
         prop_saduria = saduria_entomon_tot/tot_prey_biom,
         prop_common = (amphipoda_tot + clupea_harengus_tot + clupeidae_tot + other_crustacea_tot + 
                          other_pisces_tot + polychaeta_tot + saduria_entomon_tot + sprattus_sprattus_tot) / tot_prey_biom,
         common_tot = (amphipoda_tot + clupea_harengus_tot + clupeidae_tot + other_crustacea_tot +
                        other_pisces_tot + polychaeta_tot + saduria_entomon_tot + sprattus_sprattus_tot)) %>% 
  filter(FR_tot > -1) # remove negative values of FR

# Plot FR_tot for all years
ggplot(cod, aes(year, FR_tot)) + 
  geom_point(size = 3, shape = 21, color = "white", fill = "gray30") + 
  stat_smooth() + 
  facet_wrap(~quarter) + 
  theme_classic(base_size = 16) +
  NULL

# Check individual stomachs with high FR values... 0.5 seems like a reasonable cutoff
cod <- cod %>% filter(FR_tot < 0.5) %>% as.data.frame()
ggplot(cod, aes(year, FR_tot)) + 
  geom_point(size = 2, shape = 21, color = "white", fill = "gray30") + 
  facet_wrap(~quarter) + 
  NULL

# Check flounder
fle <- fle %>% filter(FR_tot < 0.2) %>% as.data.frame()
ggplot(fle, aes(year, FR_tot)) + 
  geom_point(size = 2, shape = 21, color = "white", fill = "gray30") + 
  facet_wrap(~quarter) + 
  NULL

# Large gaps, group by time period and make rain-cloud plot
# https://www.cedricscherer.com/2021/06/06/visualizing-distributions-with-raincloud-plots-and-how-to-create-them-with-ggplot2/
cod <- cod %>% 
  mutate(time_period = "1963-1978",
         time_period = ifelse(year > 1980, "1986-1990", time_period),
         time_period = ifelse(year > 1990, "2006-2020", time_period)) %>% 
  mutate(quarter_fact = ifelse(quarter == 1, "Quarter 1", "Quarter 4"))

p1 <- ggplot(filter(cod, quarter == 1), aes(time_period, FR_tot, color = time_period, fill = time_period)) + 
  ggdist::stat_halfeye(adjust = .5, width = 0.8, .width = 0, justification = -.1, point_colour = NA, alpha = 0.5) + 
  geom_point(shape = 21, color = "white", size = 1.3, alpha = .2, position = position_jitter(seed = 1, width = 0.1)) + 
  geom_boxplot(width = .15, outlier.shape = NA, fill = "white", alpha = 0.2) +  
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  guides(color = FALSE, fill = FALSE) +
  labs(x = "", y = "") +
  coord_cartesian(ylim = c(0, 5)) +
  coord_flip() +
  geom_text(data = cod %>% filter(quarter == 1) %>% group_by(time_period, quarter) %>% summarise(n = n()),
            aes(y = 0.25, x = time_period, label = glue::glue("n = {n}")), nudge_x = 0.3) +
  theme(legend.position = "bottom") + 
  theme_classic(base_size = 10) +
  ggtitle("Quarter 1") +
  NULL

p2 <- ggplot(filter(cod, quarter == 4), aes(time_period, FR_tot, color = time_period, fill = time_period)) + 
  ggdist::stat_halfeye(adjust = .5, width = 0.8, .width = 0, justification = -.1, point_colour = NA, alpha = 0.5) + 
  geom_point(shape = 21, color = "white", size = 1.3, alpha = .2, position = position_jitter(seed = 1, width = 0.1)) + 
  geom_boxplot(width = .15, outlier.shape = NA, fill = "white", alpha = 0.2) +  
  scale_color_brewer(palette = "Dark2") +
  scale_fill_brewer(palette = "Dark2") +
  guides(color = FALSE, fill = FALSE) +
  labs(x = "", y = "Feeding ratio") +
  coord_cartesian(ylim = c(0, 5)) +
  coord_flip() +
  geom_text(data = cod %>% filter(quarter == 4) %>% group_by(time_period, quarter) %>% summarise(n = n()),
            aes(y = 0.25, x = time_period, label = glue::glue("n = {n}")), nudge_x = 0.3) +
  theme(legend.position = "bottom") + 
  theme_classic(base_size = 10) +
  ggtitle("Quarter 4") +
  NULL

p1 / p2

# How many of the old samples don't have coordinates?
# Too many!
t <- cod %>% 
  filter(time_period == "1963-1978") %>% 
  drop_na(lat, long)
```

## Add in density and depth covariates

```{r test analysis}
# First read the density models and predict the values
mcod2 <- readRDS("output/mcod2.rds")
mfle2 <- readRDS("output/mfle2.rds")

# Make predictions onto the stomach data defined earlier (1 row per stomach and prey?)

# Add depth and rename coordinates to match the data used for fitting the density model
# Read the tifs
west <- raster("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_condition/data/depth_geo_tif/D5_2018_rgb-1.tif")
#plot(west)

east <- raster("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/cod_condition/data/depth_geo_tif/D6_2018_rgb-1.tif")
# plot(east)

dep_rast <- raster::merge(west, east)

colnames(cod)
colnames(fle)
cod$depth <- extract(dep_rast, cod[, 27:26])
fle$depth <- extract(dep_rast, fle[, 27:26])

# Convert to depth (instead of elevation)
ggplot(cod, aes(depth)) + geom_histogram()
cod$depth <- (cod$depth - max(drop_na(cod)$depth)) *-1
ggplot(cod, aes(depth)) + geom_histogram()

fle$depth <- (fle$depth - max(drop_na(fle)$depth)) *-1

cod <- cod %>% rename("X" = "x", "Y" = "y")
cod <- cod %>% mutate(year = as.integer(year))

fle <- fle %>% rename("X" = "x", "Y" = "y")
fle <- fle %>% mutate(year = as.integer(year))

# Standardize depth to the DENSITY data, not this data set
density_dat <- readr::read_csv("https://raw.githubusercontent.com/maxlindmark/cod_condition/master/data/for_analysis/mdat_cpue.csv")

# Rename to match variables in the density model
cod <- cod %>% mutate(depth_sc = (depth - mean(density_dat$depth)) / sd(density_dat$depth))
fle <- fle %>% mutate(depth_sc = (depth - mean(density_dat$depth)) / sd(density_dat$depth))

cod2 <- cod %>% filter(year < 2020 & year > 1992) # Remove this after I've refitted the models with 2020!
cod_old <- cod %>% filter(year < 1993) # Filter the old data so that we can rbind it later
fle2 <- fle %>% filter(year < 2020) # Remove this after I've refitted the models with 2020!

# Now predict using the density models
cod_stomach_predcod_density <- predict(mcod2, newdata = dplyr::select(cod2, depth_sc, year, X, Y))
cod_stomach_predfle_density <- predict(mfle2, newdata = dplyr::select(cod2, depth_sc, year, X, Y))

fle_stomach_predcod_density <- predict(mcod2, newdata = dplyr::select(fle2, depth_sc, year, X, Y))
fle_stomach_predfle_density <- predict(mfle2, newdata = dplyr::select(fle2, depth_sc, year, X, Y))

cod2$predcod_density <- exp(cod_stomach_predcod_density$est)
cod2$predfle_density <- exp(cod_stomach_predfle_density$est)

fle2$predcod_density <- exp(fle_stomach_predcod_density$est)
fle2$predfle_density <- exp(fle_stomach_predfle_density$est)

# Add scaled predicted densities to the stomach data
cod2 <- cod2 %>%
  mutate(predcod_density_sc = (predcod_density - mean(predcod_density))/sd(predcod_density),
         predfle_density_sc = (predfle_density - mean(predfle_density))/sd(predfle_density))

fle2 <- fle2 %>%
  mutate(predcod_density_sc = (predcod_density - mean(predcod_density))/sd(predcod_density),
         predfle_density_sc = (predfle_density - mean(predfle_density))/sd(predfle_density))

# Add the old data back using bind_rows so that density estimates get NA
cod2 <- bind_rows(cod2, cod_old)
```

## Save data for further analysis

```{r save data}
colnames(cod)

cod_save <- cod2 %>% dplyr::select(FR_tot, FR_sad, FR_spr, saduria_entomon_tot, tot_prey_biom, common_tot, unique_pred_id,
                                   year, quarter, time_period, quarter_fact, pred_weight_g, pred_cm,
                                   predator_spec, predcod_density, predfle_density, predcod_density_sc,
                                   predfle_density_sc, depth, X, Y, lat, long, ices_rect, cruise)

fle_save <- fle2 %>% dplyr::select(FR_tot, FR_sad, FR_spr, saduria_entomon_tot, tot_prey_biom, common_tot, unique_pred_id,
                                   year, quarter, pred_weight_g, pred_cm,
                                   predator_spec, predcod_density, predfle_density, predcod_density_sc,
                                   predfle_density_sc, depth, X, Y, lat, long, ices_rect, cruise)

write.csv(cod_save, "data/cod_diet_analysis.csv")
write.csv(fle_save, "data/fle_diet_analysis.csv")
```

## Extra: explore response variables

```{r}
# How does stomach content scale with size? Probably a little!
ggplot(cod, aes(pred_cm, FR_tot, color = time_period)) +
  geom_point(alpha = 0.4) + 
  facet_wrap(~time_period) +
  stat_smooth(color = "black")

ggplot(fle, aes(pred_cm, FR_tot)) +
  geom_point(alpha = 0.4) + 
  stat_smooth(color = "black")

# r plot cod stomach against density
# Common prey
p1 <- ggplot(cod2, aes(predcod_density_sc, prop_common)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()
  
p2 <- ggplot(cod2, aes(predcod_density_sc, common_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p3 <- ggplot(cod2, aes(predfle_density_sc, prop_common)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p4 <- ggplot(cod2, aes(predfle_density_sc, common_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p5 <- ggplot(cod2, aes(predfle_density_sc + predcod_density_sc, prop_common)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p6 <- ggplot(cod2, aes(predfle_density_sc + predcod_density_sc, common_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

(p1|p2) / (p3|p4) / (p5|p6) + plot_annotation(title = "Cod stomachs", 
                                                  theme = theme(plot.title = element_text(size = 16)))

# Saduria
p7 <- ggplot(cod2, aes(predcod_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p8 <- ggplot(cod2, aes(predcod_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p9 <- ggplot(cod2, aes(predfle_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p10 <- ggplot(cod2, aes(predfle_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p11 <- ggplot(cod2, aes(predfle_density_sc + predcod_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p12 <- ggplot(cod2, aes(predfle_density_sc + predcod_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

(p7|p8) / (p9|p10) / (p11|p12) + plot_annotation(title = "Cod stomachs", 
                                                  theme = theme(plot.title = element_text(size = 16)))

# Total stomach content (FR)
p13 <- ggplot(cod2, aes(predcod_density_sc, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p14 <- ggplot(cod2, aes(predfle_density_sc, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p15 <- ggplot(cod2, aes(predfle_density_sc + predcod_density, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

(p13/p14/p15) + plot_annotation(title = "Cod stomachs", theme = theme(plot.title = element_text(size = 16)))

# Closer inspection of some of the plots...
ggplot(cod2, aes(predfle_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm") + 
  ggtitle("prop saduria vs fle density")

ggplot(cod2, aes(predfle_density, tot_prey_biom/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth() + 
  ggtitle("g/g tot. stomach vs fle density")

ggplot(cod2, aes(predfle_density + predcod_density, tot_prey_biom/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth() + 
  ggtitle("g/g tot. stomach vs fle  + coddensity")

## Plot flounder stomach against density

# Common prey
p1 <- ggplot(fle2, aes(predcod_density_sc, prop_common)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p2 <- ggplot(fle2, aes(predcod_density_sc, common_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p3 <- ggplot(fle2, aes(predfle_density_sc, prop_common)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p4 <- ggplot(fle2, aes(predfle_density_sc, common_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p5 <- ggplot(fle2, aes(predfle_density_sc + predcod_density_sc, prop_common)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p6 <- ggplot(fle2, aes(predfle_density_sc + predcod_density_sc, common_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

(p1|p2) / (p3|p4) / (p5|p6) + plot_annotation(title = "Flounder stomachs", 
                                                  theme = theme(plot.title = element_text(size = 16)))

# Saduria
p7 <- ggplot(fle2, aes(predcod_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p8 <- ggplot(fle2, aes(predcod_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p9 <- ggplot(fle2, aes(predfle_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p10 <- ggplot(fle2, aes(predfle_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p11 <- ggplot(fle2, aes(predfle_density_sc + predcod_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p12 <- ggplot(fle2, aes(predfle_density_sc + predcod_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

(p7|p8) / (p9|p10) / (p11|p12) + plot_annotation(title = "Flounder stomachs", 
                                                  theme = theme(plot.title = element_text(size = 16)))

# FR
p13 <- ggplot(fle2, aes(predcod_density_sc, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p14 <- ggplot(fle2, aes(predfle_density_sc, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

p15 <- ggplot(fle2, aes(predfle_density_sc + predcod_density, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth()

(p13/p14/p15) + plot_annotation(title = "Flounder stomachs", theme = theme(plot.title = element_text(size = 16)))
```

## More in depth plots...

```{r more in depth plots}
# Does it seem like proportions of the diet changes with density, but not the total amount of food?
# Check saduria and flounder for instance.
pp7 <- ggplot(fle2, aes(predcod_density_sc, prop_saduria)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm")

pp8 <- ggplot(filter(fle2, (saduria_entomon_tot/pred_weight_g) < 0.1),
             aes(predcod_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm")

pp13 <- ggplot(filter(fle2, (saduria_entomon_tot/pred_weight_g) < 0.1),
              aes(predcod_density_sc, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm")

ppfle <- pp7/pp8/pp13 +
  plot_layout(ncol = 3) + 
  plot_annotation(title = "Flounder stomachs", theme = theme(plot.title = element_text(size = 16)))

# And that cod density is unaffected (or less at least)
p7 <- ggplot(filter(cod2, (saduria_entomon_tot/pred_weight_g) < 0.02 & predfle_density_sc < 2),
             aes(predfle_density_sc, prop_saduria)) + # Crop it up a little!
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm")

p8 <- ggplot(filter(cod2, (saduria_entomon_tot/pred_weight_g) < 0.02 & predfle_density_sc < 2),
             aes(predfle_density_sc, saduria_entomon_tot/pred_weight_g)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm")

p13 <- ggplot(filter(cod2, (saduria_entomon_tot/pred_weight_g) < 0.02 & predfle_density_sc < 2 & FR_tot < 0.5),
              aes(predfle_density_sc, FR_tot)) + 
  geom_point(size = 2, shape = 21, fill = "black", color = "white", alpha = 0.8) + 
  stat_smooth(method = "lm")

ppcod <- p7/p8/p13 +
  plot_layout(ncol = 3) +
  plot_annotation(title = "Cod stomachs", theme = theme(plot.title = element_text(size = 16)))

ppfle / ppcod

# What does it mean? Yes, the proportion *may* be negatively affected by densities, 
# but the food content is not, which I guess would matter for condition
```

## Extra: try and reproduce Haases figure

```{r reproduce haase figure}
# Now, group by survey and Quarter, select only the main groups (as Haase) and see if it resembles the
# previous results.
## Reproduce Haase figures with biomass proportions

# Try to reproduce Haase et al!
# Aggregate across predator individuals and convert to long data for plotting
cod2 <- cod %>%
  drop_na(pred_cm_class) %>% # This is because not all predators have length
  filter(cruise %in% c("BITS", "BITS-1", "BITS-2")) %>%
  filter(year %in% c(2015, 2016, 2017)) %>%
  filter(source == "Kevin's MSC") %>% 
  filter(!pred_cm_class == "(0,6]") %>% 
  group_by(quarter, pred_cm_class) %>% 
  summarise(sprattus_sprattus_tot_all = sum(sprattus_sprattus_tot),
            saduria_entomon_tot_all = sum(saduria_entomon_tot),
            mysidae_tot_all = sum(mysidae_tot),
            clupea_harengus_tot_all = sum(clupea_harengus_tot),
            sprattus_sprattus_tot_all = sum(sprattus_sprattus_tot),
            gobiidae_tot_all = sum(gobiidae_tot),
            gadiformes_tot_all = sum(gadiformes_tot),
            other_pisces_tot_all = sum(other_pisces_tot),
            polychaeta_tot_all = sum(polychaeta_tot)) %>% 
  ungroup() %>% 
  pivot_longer(3:10) %>% 
  group_by(quarter, pred_cm_class) %>% 
  mutate(percent = value/sum(value)) %>%
  ungroup()
  
# So much herring for small cod?
# A 20 cm cod weighs approx 100 g. Can it have 20g of herring in the stomach?
#small_cod <-
d %>%
  filter(Pred.size.mm < 200 & Prey.sp.code %in% c("clupea harengus", "Clupea harengus")) %>% 
  dplyr::select(Prey.weight, Prey.sp.code, Unique.pred.id, Pred.size.mm)

d_wide4 %>% filter(unique_pred_id == "2016_1_73_735_COD") %>% as.data.frame()
d %>% filter(Unique.pred.id == "2016_1_73_735_COD") %>% as.data.frame()

# Check sample sizes per size class (numbers below bars in Kevins figures)
cod %>%
  drop_na(pred_cm_class) %>% # This is because not all predators have length
  filter(cruise %in% c("BITS", "BITS-1", "BITS-2")) %>%
  filter(year %in% c(2015, 2016, 2017)) %>%
  filter(source == "Kevin's MSC") %>% 
  filter(!pred_cm_class == "(0,6]") %>% 
  group_by(quarter, pred_cm_class) %>% 
  summarise(n = n())
# I seem to have more data...  

# Check Kevin's raw data... 
kev <- read.csv("/Users/maxlindmark/Desktop/R_STUDIO_PROJECTS/bentfish/data/stomach_data/Master_Kevin_updated.csv", sep = ";")
head(kev)

kev$prey.weight <- as.numeric(gsub(",", ".", gsub("\\.", "", kev$prey.weight)))

kev %>% 
  filter(lengthclass == "Lc6-20" & pred.code == "COD" & year %in% c(2015, 2016, 2017) & quarter == 1) %>% 
  drop_na(prey.sp.code) %>%
  drop_na(prey.weight) %>%
  group_by(prey.sp.code) %>% 
  summarise(tot_weight_by_prey = sum(prey.weight)) %>% 
  arrange(desc(tot_weight_by_prey)) %>% 
  as.data.frame()

# OK so probably Kevin made some additional filter, because I also have a larger sample size
```
